---
title: "MSc multiclass datasets selection.Rmd"
author: "Hubert Ruczyński"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    theme: lumen
    toc_depth: 3
    number_sections: yes
    code_folding: hide
    latex_engine: xelatex
---

```{css, echo=FALSE}
body .main-container {
  max-width: 1820px !important;
  width: 1820px !important;
}
body {
  max-width: 1820px !important;
  width: 1820px !important;
  font-family: Helvetica !important;
  font-size: 16pt !important;
}
h1,h2,h3,h4,h5,h6{
  font-size: 24pt !important;
}
```

# Imports

We import the forester package to use the check_data function.

```{r message=FALSE, warning=FALSE}
library(forester)
```

# Loading data

We load the data from the RData files.

```{r}
CC18 <- readRDS("CC18.RData")
regression <- readRDS("regression_bench.RData")
```

# Multiclass tasks selection

At first we check which CC18 datasets are multiclass, as the benhcmark cosnists of both bianry and multilcass classification tasks.

```{r}
multiclass_indexes <-c()
for (i in 1:length(CC18)) {
  if (length(levels(CC18[[i]]$class)) > 2) {
    multiclass_indexes <- c(multiclass_indexes, i)
  }
}
multiclass_indexes
multiclass_CC18 <- CC18[multiclass_indexes]
```

# Selecting a subset of tasks

Later, we analyse the sizes of the multiclass datasets, and ensure that we choose the representants with different characteristics, and reasonable sizes (not too big or too small).

```{r}
for (i in 1:length(multiclass_CC18)) {
  cat('Dataset Index:', i, '\n  Name:', names(multiclass_CC18)[i], '\n  Dimensionality:', dim(multiclass_CC18[[i]]), '\n')
}
```

Eventually we end up with the following selection of datasets:

```{r}
small_idx <- c(2, 3, 4, 5, 7, 10, 15, 16, 17, 21)
multiclass_CC18_small <- multiclass_CC18[small_idx]
multiclass_CC18 <- multiclass_CC18_small[c(1, 4, 6, 7, 10)]
for (i in 1:length(multiclass_CC18)) {
  cat('Dataset Index:', i, '\n  Name:', names(multiclass_CC18)[i], '\n  Dimensionality:', dim(multiclass_CC18[[i]]), '\n')
}
```

# Adding wine_quality task

However, as a mistake, one of the regression datasets called `wine_quality` is actually a multiclass task, thus we also add it here

```{r}
multiclass_CC18[[6]] <- regression[[2]]
names(multiclass_CC18)[6] <- "wine_quality"
for (i in 1:length(multiclass_CC18)) {
  cat('Dataset Index:', i, '\n  Name:', names(multiclass_CC18)[i], '\n  Dimensionality:', dim(multiclass_CC18[[i]]), '\n')
}
```

# Data check

Additionally, we calculate the foresters data check for all tasks.

```{r warning=FALSE}
for (i in 1:length(multiclass_CC18)) {
  cat('Dataset Index:', i, '\n  Name:', names(multiclass_CC18)[i], '\n  Dimensionality:', dim(multiclass_CC18[[i]]), '\n\n')
  if (i != 6) {
    check_data(multiclass_CC18[[i]], 'class')
  } else {
    check_data(multiclass_CC18[[i]], 'quality')
  }
}
```


# Saving the outcomes

```{r}
saveRDS(multiclass_CC18, "multiclass_CC18.RData")
```

