---
title: "MSc_altered_datasets_creation"
author: "Hubert Ruczyński"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    theme: lumen
    toc_depth: 3
    number_sections: yes
    code_folding: hide
    latex_engine: xelatex
---

```{css, echo=FALSE}
body .main-container {
  max-width: 1820px !important;
  width: 1820px !important;
}
body {
  max-width: 1820px !important;
  width: 1820px !important;
  font-family: Helvetica !important;
  font-size: 16pt !important;
}
h1,h2,h3,h4,h5,h6{
  font-size: 24pt !important;
}
```

# Imports

We import the forester package to use the check_data function.

```{r message=FALSE, warning=FALSE}
library(forester)
```

# Loading data

We load the data from the RData files.

```{r}
MSc_binary_CC18      <- readRDS("binary_CC18.RData")
MSc_regression_bench <- readRDS("regression_bench.RData")
MSc_multiclass_CC18  <- readRDS("multiclass_CC18.RData")

MSc_regression_bench <- MSc_regression_bench[c(1, 3, 4, 6, 7)]
```

# Altering function

As the original datasets come from the benchmarks, their quality is much higer than in the case of regular ML tasks. Thus we alter the datasets in order to create a lower-quality, more real-life examples.

To achieve that we introduce the following changes:

-   Adding ID column,

-   Adding static columns,

-   Duplicating existing columns,

-   Introducing the missing values for 3 columns where 5%, 10%, and 15% of observations are missing.

```{r}
alter_df <- function(df) {
  org_df_id <- 1:(ncol(df) - 1)
  # Adding ID column
  df$ID <- 1:nrow(df)
  # Adding static columns
  df$static_obvious <- rep(1, nrow(df))
  df$static_less_obvious <- c(rep('a', as.integer(nrow(df) * 0.995)), rep('b', (nrow(df) - as.integer(nrow(df) * 0.995))))
  # Duplicating existing columns
  set.seed(123)
  id <- sample(org_df_id, 2)
  df$duplicate_1 <- df[, id[1]]
  df$duplicate_2 <- df[, id[2]]
  # Introducing the missing values
  row_idx <- 1:nrow(df)
  set.seed(234)
  id <- sample(org_df_id[!org_df_id %in% id], 3)
  set.seed(345)
  miss_idx <- sample(row_idx, nrow(df) * 0.05)
  df[miss_idx, id[1]] <- NA
  set.seed(456)
  miss_idx <- sample(row_idx, nrow(df) * 0.1)
  df[miss_idx, id[2]] <- NA
  set.seed(567)
  miss_idx <- sample(row_idx, nrow(df) * 0.15)
  df[miss_idx, id[3]] <- NA
  
  return(df)
}
```

# Alternation

We alter the selected subset of datasets from all tasks.

```{r}
MSc_binary_CC18$`credit-g-mod`       <- alter_df(MSc_binary_CC18$`credit-g`)
MSc_binary_CC18$`phoneme-mod`        <- alter_df(MSc_binary_CC18$phoneme)
MSc_regression_bench$`elevators-mod` <- alter_df(MSc_regression_bench$elevators)
MSc_regression_bench$`kin8nm-mod`    <- alter_df(MSc_regression_bench$kin8nm)
MSc_multiclass_CC18$`satimage-mod`   <- alter_df(MSc_multiclass_CC18$satimage)
MSc_multiclass_CC18$`car-mod`        <- alter_df(MSc_multiclass_CC18$car)
MSc_binary_CC18      <- MSc_binary_CC18[c(1, 2, 3, 4, 5, 19, 25, 26, 36, 37)]
```

# Data check

Additionally, we calculate the foresters data check for all modified tasks.

```{r}
cat('Credit-g-mod\n')
s <- check_data(MSc_binary_CC18$`credit-g-mod`, 'class')
cat('Phoneme-g-mod\n')
s <- check_data(MSc_binary_CC18$phoneme, 'Class')
cat('Elevators-mod\n')
s <- check_data(MSc_regression_bench$elevators, 'Goal')
cat('Kin8nm-mod\n')
s <- check_data(MSc_regression_bench$kin8nm, 'y')
cat('Satimage-mod\n')
s <- check_data(MSc_multiclass_CC18$satimage, 'class')
cat('Car-mod\n')
s <- check_data(MSc_multiclass_CC18$car, 'class')
```

# Saving altered datasets

```{r}
MSc_binary_CC18      <- MSc_binary_CC18[c(1, 2, 3, 4, 5, 19, 25, 26, 36, 37)]
saveRDS(MSc_binary_CC18,      "MSc_binary_CC18.RData")
saveRDS(MSc_regression_bench, "MSc_regression_bench.RData")
saveRDS(MSc_multiclass_CC18,  "MSc_multiclass_CC18.RData")
```
