---
title: "forester_benchmark"
author: "Hubert Ruczyński"
date: "`r Sys.Date()`"
output: html_document
---

# Downloads

The necessary downloads required for the forester package to work properly, if downloaded, the user can skip this part.

```{r}
install.packages("devtools")
devtools::install_github("ModelOriented/forester")
devtools::install_github('catboost/catboost', subdir = 'catboost/R-package')
devtools::install_github('ricardo-bion/ggradar', dependencies = TRUE)
install.packages('tinytex')
tinytex::install_tinytex()
```

To install the h2o package, we recommend to see the resources from its authors under the link: <http://h2o-release.s3.amazonaws.com/h2o/master/1735/docs-website/Ruser/Rinstall.html>, however the basic option is to run the code below. Note that the users need the Java installed on the machine.

```{r}
install.packages("h2o")
```

# Initialization

Importing the necessary libraries, let's notice that the user has to install the H2O package before, and to do that one has to have Java installed on the machine.

```{r}
library(OpenML)
library(forester)
library(h2o)
library(tictoc)
library(farff)
```

# Data preparations

## Getting the datasets

### Binary classification

Downloading whole OpenML-CC18 benchmark and saving it in the working directory.

```{r}
i          <- 0
bsuite     <- getOMLStudy('OpenML-CC18')
task.ids   <- extractOMLStudyIds(bsuite, 'task.id')
CC18       <- list()
df_names   <- c() 
for (task.id in task.ids) {
  task <- getOMLTask(task.id)
  data <- as.data.frame(task)
  i    <- i + 1
  cat('Data set id: ', i, 'Data set name: ', task$input$data.set$desc$name, '\n')
  df_names  <- c(df_names, task$input$data.set$desc$name)
  CC18[[i]] <- data
}
names(CC18) <- df_names
saveRDS(CC18, file = "CC18.RData")
```

### Regression

Loading widely used datasets from OpenML.

```{r}
wind              <- readARFF('regression_datasets/wind.arff') # Not regression task
communities_crime <- readARFF('regression_datasets/phpeZQVCe.arff') # ViolentCrimesPerPop
bank32nh          <- readARFF('regression_datasets/phpYYZ4Qc.arff') # Target: rej
wine_quality      <- readARFF('regression_datasets/wine_quality.arff') # Target: quality
Mercedes_Benz     <- readARFF('regression_datasets/dataset.arff') # Target: y (2nd col)
Mercedes_Benz_y   <- Mercedes_Benz$y
Mercedes_Benz     <- Mercedes_Benz[, -2]
Mercedes_Benz$y   <- Mercedes_Benz_y # the last one
kin8nm            <- readARFF('regression_datasets/dataset_2175_kin8nm.arff') # Target: y
pol               <- readARFF('regression_datasets/dataset_2187_pol.arff') # Target: foo (really streched)
planes2d          <- readARFF('regression_datasets/dataset_2201_2dplanes.arff') # Target: y
elevators         <- readARFF('regression_datasets/dataset_2202_elevators.arff') # Target: Goal
stock             <- readARFF('regression_datasets/dataset_2209_stock.arff') # Not regression task

regression_bench <- list()

regression_bench[[1]]  <- as.data.frame(wind)
regression_bench[[2]]  <- as.data.frame(communities_crime)
regression_bench[[3]]  <- as.data.frame(bank32nh)
regression_bench[[4]]  <- as.data.frame(wine_quality)
regression_bench[[5]]  <- as.data.frame(Mercedes_Benz)
regression_bench[[6]]  <- as.data.frame(kin8nm)
regression_bench[[7]]  <- as.data.frame(pol)
regression_bench[[8]]  <- as.data.frame(planes2d)
regression_bench[[9]]  <- as.data.frame(elevators)
regression_bench[[10]] <- as.data.frame(stock)

names(regression_bench) <- c('wind', 'us_crime', 'bank32nh', 'wine_quality', 
                             'Mercedes_Benz_Greener_Manufacturing', 'kin8nm', 'pol', 
                             '2dplanes', 'elevators', 'stock')

regression_bench <- regression_bench[2:9]
```

## Data sets exploration

Data sets exploration function provides us with some basic information about the data sets used in a benchmark, such as number of rows, columns, target values, task name, and data set id.

```{r}
datasets_exploration <- function(tasks_data) {
  df_id       <- c()
  y_name      <- c()
  df_name     <- c()
  y_nr_levels <- c()
  ncols       <- c()
  nrows       <- c()
  for (i in 1:length(tasks_data)) {
    df_id       <- c(df_id, i)
    df_name     <- c(df_name, names(tasks_data)[i])
    y_name      <- c(y_name, colnames(tasks_data[[i]])[ncol(tasks_data[[i]])])
    y_nr_levels <- c(y_nr_levels, length(levels(tasks_data[[i]][, ncol(tasks_data[[i]])])))
    ncols       <- c(ncols, ncol(tasks_data[[i]]))
    nrows       <- c(nrows, nrow(tasks_data[[i]]))
  }
  
  df_exploration <- data.frame(df_id, df_name, y_nr_levels, ncols, nrows, y_name)
  return(df_exploration)
}
```

## Exploration of the CC18

```{r}
exploration <- datasets_exploration(CC18)
cat('Summary of ncols: \n')
summary(exploration$ncols)
cat('Summary of nrows: \n')
summary(exploration$nrows)
exploration
```

## Binary datasets selection

As the forester package doesn't work on the multiclass classification, we have to limit ourselves to the binary classifications tasks only, and save the dataset in a working directory, so we don't have to download everything again.

```{r}
CC18              <- readRDS("CC18.RData")
binary_CC18       <- list()
binary_CC18_names <- c()
j <- 1

for (i in 1:length(CC18)) {
  if (length(levels(CC18[[i]][, ncol(CC18[[i]])])) == 2) {
    binary_CC18[[j]]  <- CC18[[i]]
    binary_CC18_names <- c(binary_CC18_names, names(CC18)[i])
    j <- j + 1
  }
}

names(binary_CC18) <- binary_CC18_names
saveRDS(binary_CC18, file = "binary_CC18.RData")
```

## Exploration of the binary CC18

```{r}
binary_CC18 <- readRDS("binary_CC18.RData")
exploration <- datasets_exploration(binary_CC18)
cat('Summary of ncols: \n')
summary(exploration$ncols)
cat('Summary of nrows: \n')
summary(exploration$nrows)
exploration[c(1, 2, 3, 4, 5, 19, 25, 26), c(2, 4, 5)]
```

## Exploration of the regression data sets

```{r}
datasets_exploration(regression_bench)
```

# Experiments on the forester package

## Binary classification

### Experiment function

The experiment function conducts a model training for the forester package. It trains the `ranger`, `decision_tree`, `lightgbm`, and `catboost` models for every dataset provided to the function. The training is repeated `reps` (=3) times, and we have to provide a `split_seed` vector of length `reps` which sets random seed for the splitting method inside the forester. Every training consists of 10 Bayesian Optimisation iterations and 10 random search evaluations. This function measures the times needed for the training of every model, so we can provide that for the h2o AutoML. the function returns the id's of the split, all models metrics on every subset and best models metrics on every subset.

```{r}
forester_experiment <- function(df_set, split_seed, bayes_iter = 10, random_evals = 10, advanced_preprocessing = FALSE, reps = 3) {
  
  best_models_train <- data.frame()
  best_models_test  <- data.frame()
  best_models_valid <- data.frame()
  
  all_models_train  <- list()
  all_models_test   <- list()
  all_models_valid  <- list()
  
  train_test_valid  <- list()
  
  list_names <- c()
  
  list_times  <- c()
  names_times <- c()
  
  tic('\n General')
  for (i in 1:length(df_set)) {
    tic(paste0('\n Iteration: ', i, ' Dataset: ', names(df_set)[i]))
    for (j in 1:reps) {
      list_times  <- c(list_times, Sys.time())
      names_times <- c(names_times, paste0('Training: ', names(df_set)[i], ' rep ', j))
      output <- train(data = df_set[[i]], 
                      y = colnames(df_set[[i]])[length(df_set[[i]])],
                      engine = c("ranger", "decision_tree", "lightgbm", "catboost"),
                      verbose = FALSE,
                      train_test_split = c(0.6, 0.2, 0.2),
                      split_seed = split_seed[j],
                      bayes_iter = bayes_iter,
                      random_evals = random_evals,
                      advanced_preprocessing = advanced_preprocessing)
      
      top_score_train            <- output$score_train[1, ]
      top_score_train$task_name  <- names(df_set)[i]
      top_score_train$rep        <- j
      
      top_score_test             <- output$score_test[1, ]
      top_score_test$task_name   <- names(df_set)[i]
      top_score_test$rep         <- j
      
      top_score_valid            <- output$score_valid[1, ]
      top_score_valid$task_name  <- names(df_set)[i]
      top_score_valid$rep        <- j
      
      best_models_train <- rbind(best_models_train, top_score_train)
      best_models_test  <- rbind(best_models_test, top_score_test)
      best_models_valid <- rbind(best_models_valid, top_score_valid)
      
      list_names <- c(list_names, paste0(names(df_set)[i], '-rep-', j))
      
      all_models_train[[(i - 1) * reps + j]]  <- data.frame(output$score_train)
      all_models_test[[(i - 1) * reps + j]]   <- data.frame(output$score_train)
      all_models_valid[[(i - 1) * reps + j]]  <- data.frame(output$score_test)
      
      train_test_valid[[(i - 1) * reps + j]]  <- list(
        train_inds = output$train_inds,
        test_inds  = output$test_inds,
        valid_inds = output$valid_inds
      )

    }
    toc()
  }
  list_times  <- c(list_times, Sys.time())
  names_times <- c(names_times, paste0('The end'))
  
  time_df <- data.frame(name = names_times, timestamp = list_times)
  
  print(list_names)
  names(all_models_train)  <- list_names
  names(all_models_test)   <- list_names
  names(all_models_valid)  <- list_names
  names(train_test_valid)  <- list_names
  toc()
  return(list(
    best_models_train = best_models_train,
    best_models_test  = best_models_test,
    best_models_valid = best_models_valid,
    all_models_train  = all_models_train,
    all_models_test   = all_models_test,
    all_models_valid  = all_models_valid,
    train_test_valid  = train_test_valid,
    time_df           = time_df
  ))
}
```

### Batch training

As training the models on the dataset is extremely time consuming (mainly because of MICE imputation and Bayesian Optimisation), we've decided to train the forester in batches, and saving the outcomes in the working directory.

```{r}
outcomes1 <- forester_experiment(head(binary_CC18, 3), c(123, 2137, 21), 10, 10, reps = 3)
saveRDS(outcomes1, file = "trained_1_3_sets_3_reps_10b_10r.RData")
```

```{r}
outcomes2 <- forester_experiment(head(binary_CC18[4:5], 3), c(123, 2137, 21), 10, 10, reps = 3)
saveRDS(outcomes2, file = "trained_4_5_sets_3_reps_10b_10r.RData")
```

```{r}
outcomes3 <- forester_experiment(head(binary_CC18[19], 3), c(123, 2137, 21), 10, 10, reps = 3)
saveRDS(outcomes3, file = "trained_19_sets_3_reps_10b_10r.RData")
```

```{r}
outcomes4 <- forester_experiment(head(binary_CC18[25:26], 3), c(123, 2137, 21), 10, 10, reps = 3)
saveRDS(outcomes4, file = "trained_25_26_sets_3_reps_10b_10r.RData")
```

## Regression

### Experiment function

```{r}
forester_experiment <- function(df_set, split_seed, bayes_iter = 25, random_evals = 10, advanced_preprocessing = FALSE, reps = 5, engine = c("ranger", "xgboost", "decision_tree", "lightgbm", "catboost")) {
  
  best_models_train <- data.frame()
  best_models_test  <- data.frame()
  best_models_valid <- data.frame()
  
  all_models_train  <- list()
  all_models_test   <- list()
  all_models_valid  <- list()
  
  train_test_valid  <- list()
  
  list_names <- c()
  
  list_times  <- c()
  names_times <- c()
  
  tic('\n General')
  for (i in 1:length(df_set)) {
    tic(paste0('\n Iteration: ', i, ' Dataset: ', names(df_set)[i]))
    #list_times  <- c(list_times, Sys.time())
    #names_times  <- c(names_times, paste0('\n Iteration: ', i, ' Dataset: ', names(df_set)[i]))
    for (j in 1:reps) {
      list_times  <- c(list_times, Sys.time())
      names_times <- c(names_times, paste0('Training: ', names(df_set)[i], ' rep ', j))
      cat(paste0('Training: ', names(df_set)[i], ' rep ', j, '\n'))
      output <- train(data = df_set[[i]], 
                      y = colnames(df_set[[i]])[length(df_set[[i]])],
                      engine = engine,
                      verbose = FALSE,
                      train_test_split = c(0.6, 0.2, 0.2),
                      split_seed = split_seed[j],
                      bayes_iter = bayes_iter,
                      random_evals = random_evals,
                      advanced_preprocessing = advanced_preprocessing)
      
      top_score_train            <- output$score_train[1, ]
      top_score_train$task_name  <- names(df_set)[i]
      top_score_train$rep        <- j
      
      top_score_test             <- output$score_test[1, ]
      top_score_test$task_name   <- names(df_set)[i]
      top_score_test$rep         <- j
      
      top_score_valid            <- output$score_valid[1, ]
      top_score_valid$task_name  <- names(df_set)[i]
      top_score_valid$rep        <- j
      
      best_models_train <- rbind(best_models_train, top_score_train)
      best_models_test  <- rbind(best_models_test, top_score_test)
      best_models_valid <- rbind(best_models_valid, top_score_valid)
      
      list_names <- c(list_names, paste0(names(df_set)[i], '-rep-', j))
      
      all_models_train[[(i - 1) * reps + j]]  <- data.frame(output$score_train)
      all_models_test[[(i - 1) * reps + j]]   <- data.frame(output$score_train)
      all_models_valid[[(i - 1) * reps + j]]  <- data.frame(output$score_test)
      
      train_test_valid[[(i - 1) * reps + j]]  <- list(
        train_inds = output$train_inds,
        test_inds  = output$test_inds,
        valid_inds = output$valid_inds
      )

    }
    toc()
  }
  list_times  <- c(list_times, Sys.time())
  names_times <- c(names_times, paste0('The end'))
  
  time_df <- data.frame(name = names_times, timestamp = list_times)
  
  print(list_names)
  names(all_models_train)  <- list_names
  names(all_models_test)   <- list_names
  names(all_models_valid)  <- list_names
  names(train_test_valid)  <- list_names
  toc()
  return(list(
    best_models_train = best_models_train,
    best_models_test  = best_models_test,
    best_models_valid = best_models_valid,
    all_models_train  = all_models_train,
    all_models_test   = all_models_test,
    all_models_valid  = all_models_valid,
    train_test_valid  = train_test_valid,
    time_df           = time_df
  ))
}
```

### Batch training

```{r cache = TRUE, warning=FALSE}
outcomes1 <- forester_experiment(regression_bench[2:3], c(123, 2137, 21), 10, 10, reps = 3, 
                                 engine = c("ranger", "xgboost", "decision_tree", "lightgbm", "catboost"))
saveRDS(outcomes1, file = "trained_reg_2_3_sets_3_reps_10b_10r.RData")
```

```{r cache = TRUE, warning=FALSE}
outcomes2 <- forester_experiment(regression_bench[5:6], c(123, 2137, 21), 10, 10, reps = 3, 
                                 engine = c("ranger", "xgboost", "decision_tree", "lightgbm", "catboost"))
saveRDS(outcomes2, file = "trained_reg_5_6_sets_3_reps_10b_10r.RData")
```

```{r cache = TRUE, warning=FALSE}
outcomes3 <- forester_experiment(regression_bench[7:8], c(123, 2137, 21), 10, 10, reps = 3, 
                                 engine = c("ranger", "xgboost", "decision_tree", "lightgbm", "catboost"))
saveRDS(outcomes3, file = "trained_reg_7_8_sets_3_reps_10b_10r.RData")
```

```{r cache = TRUE, warning=FALSE}
outcomes3 <- forester_experiment(regression_bench[7:8], c(123, 2137, 21), 10, 10, reps = 3, 
                                 engine = c("ranger", "xgboost", "decision_tree", "lightgbm", "catboost"))
saveRDS(outcomes3, file = "trained_reg_7_8_sets_3_reps_10b_10r.RData")
```

# Experiments on the H2O package

## Evaluation metrics

```{r}
model_performance_auc <- function(predicted, observed) {
  tpr_tmp <- tapply(observed, predicted, sum)
  TPR     <- c(0, cumsum(rev(tpr_tmp))) / sum(observed)
  fpr_tmp <- tapply(1 - observed, predicted, sum)
  FPR     <- c(0, cumsum(rev(fpr_tmp))) / sum(1 - observed)
  auc     <- sum(diff(FPR) * (TPR[-1] + TPR[-length(TPR)]) / 2)
  
  return(auc)
}

model_performance_recall <- function(tp, fp, tn, fn) {
  return(tp / (tp + fn))
}

model_performance_precision <- function(tp, fp, tn, fn) {
  return(tp / (tp + fp))
}

model_performance_f1 <- function(tp, fp, tn, fn) {
  recall    <- tp / (tp + fn)
  precision <- tp / (tp + fp)
  return(2 * (precision * recall) / (precision + recall))
}

model_performance_accuracy <- function(tp, fp, tn, fn) {
  return((tp + tn) / (tp + fp + tn + fn))
}

model_performance_mse <- function(predicted, observed) {
  mean((predicted - observed) ^ 2, na.rm = TRUE)
}

model_performance_rmse <- function(predicted, observed) {
  sqrt(mean((predicted - observed) ^ 2, na.rm = TRUE))
}

model_performance_r2 <- function(predicted, observed) {
  1 - model_performance_mse(predicted, observed) / model_performance_mse(mean(observed), observed)
}

model_performance_mad <- function(predicted, observed) {
  median(abs(predicted - observed))
}

model_performance_mae <- function(predicted, observed) {
  mean(abs(predicted - observed))
}
```

## Experiment function

### Binary classification

The experiments on the h2o consisted of giving them the same, unprocessed data sets as for the forester, and training the h2o 3 times with basic parameters and the runtimes equal to the ones needed by the forester. As the outcomes we obtain the metrics for the best models from the h2o package.

```{r}
h2o_experiment <- function(out_object, runtimes, dataset, reps, limit = 99999) {
  
  localH2O = h2o.init()
  
  best_models_train <- data.frame()
  best_models_test  <- data.frame()
  best_models_valid <- data.frame()
  
  list_times  <- c()
  names_times <- c()
  
  for (i in 1:min(length(out_object$train_test_valid), limit)) {
    list_times  <- c(list_times, Sys.time())
    names_times <- c(names_times, paste0('Training ', i, ' h2o.'))
    j     <- ceiling(i / reps)
    split <- list(
      train = dataset[[j]][out_object$train_test_valid[[i]]$train_inds,],
      test  = dataset[[j]][out_object$train_test_valid[[i]]$test_inds,],
      valid = dataset[[j]][out_object$train_test_valid[[i]]$valid_inds,]
    )
    
    train_H2O <- as.h2o(split$train)
    test_H2O  <- as.h2o(split$test)
    valid_H2O <- as.h2o(split$valid)
    
    y <- colnames(dataset[[j]])[ncol(dataset[[j]])]
    x <- setdiff(names(train_H2O), y)
    
    aml <- h2o.automl(x = x, 
                      y = y,
                      training_frame = train_H2O,
                      max_runtime_secs = runtimes[i])
    
    pred_train <- h2o.predict(aml, train_H2O)
    pred_test  <- h2o.predict(aml, test_H2O)
    pred_valid <- h2o.predict(aml, valid_H2O)
    
    eval <- function(pred, obs, dataset, i) {
      observed    <- as.integer(as.factor(as.vector(obs[, length(obs)])))
      predictions <- as.integer(as.factor(as.vector(pred[, 1])))
      accuracy    <- sum(pred[, 1] == obs[, length(obs)]) / nrow(obs)
      auc         <- model_performance_auc(predictions - 1, observed - 1)
      task_name   <- dataset$best_models_train$task_name[i]
      rep         <- dataset$best_models_train$rep[i]
      
      tp <- sum((observed == 2) * (as.numeric(unlist(predictions)) == 2))
      fp <- sum((observed == 1) * (as.numeric(unlist(predictions)) == 2))
      tn <- sum((observed == 1) * (as.numeric(unlist(predictions)) == 1))
      fn <- sum((observed == 2) * (as.numeric(unlist(predictions)) == 1))
      f1 <- model_performance_f1(tp, fp, tn, fn)
      
      df <- data.frame(task_name = task_name, rep = rep, accruacy = accuracy, auc = auc, f1 = f1)
      return(df)
    }

    best_models_train <- rbind(best_models_train, eval(pred_train, train_H2O, out_object, i))
    best_models_test  <- rbind(best_models_test, eval(pred_test, test_H2O, out_object, i))
    best_models_valid <- rbind(best_models_valid, eval(pred_valid, valid_H2O, out_object, i))
  }
  
  list_times  <- c(list_times, Sys.time())
  names_times <- c(names_times, paste0('The end'))
  
  time_df <- data.frame(name = names_times, timestamp = list_times)
  
  return(list(
    best_models_train = best_models_train,
    best_models_test  = best_models_test,
    best_models_valid = best_models_valid,
    time_df           = time_df
  ))
}
```

### Regression

```{r}
h2o_experiment_reg <- function(out_object, runtimes, dataset, reps, limit = 99999) {
  
  localH2O = h2o.init()
  
  best_models_train <- data.frame()
  best_models_test  <- data.frame()
  best_models_valid <- data.frame()
  
  list_times  <- c()
  names_times <- c()
  
  for (i in 1:min(length(out_object$train_test_valid), limit)) {
    list_times  <- c(list_times, Sys.time())
    names_times <- c(names_times, paste0('Training ', i, ' h2o.'))
    j     <- ceiling(i / reps)
    split <- list(
      train = dataset[[j]][out_object$train_test_valid[[i]]$train_inds,],
      test  = dataset[[j]][out_object$train_test_valid[[i]]$test_inds,],
      valid = dataset[[j]][out_object$train_test_valid[[i]]$valid_inds,]
    )
    
    train_H2O <- as.h2o(split$train)
    test_H2O  <- as.h2o(split$test)
    valid_H2O <- as.h2o(split$valid)
    
    y <- colnames(dataset[[j]])[ncol(dataset[[j]])]
    x <- setdiff(names(train_H2O), y)
    
    aml <- h2o.automl(x = x, 
                      y = y,
                      training_frame = train_H2O,
                      max_runtime_secs = runtimes[i])
    
    pred_train <- h2o.predict(aml, train_H2O)
    pred_test  <- h2o.predict(aml, test_H2O)
    pred_valid <- h2o.predict(aml, valid_H2O)
    
    eval <- function(pred, obs, dataset, i) {
      observed    <- as.numeric(as.vector(obs[, length(obs)]))
      predictions <- as.numeric(as.vector(pred))
      task_name   <- dataset$best_models_train$task_name[i]
      rep         <- dataset$best_models_train$rep[i]
      
      rmse        <- model_performance_rmse(predictions, observed)
      mse         <- model_performance_mse(predictions, observed)
      r2          <- model_performance_r2(predictions, observed)
      mae         <- model_performance_mae(predictions, observed)
      
      df <- data.frame(task_name = task_name, rep = rep, rmse = rmse, mse = mse, r2 = r2, mae = mae)
      return(df)
    }

    best_models_train <- rbind(best_models_train, eval(pred_train, train_H2O, out_object, i))
    best_models_test  <- rbind(best_models_test, eval(pred_test, test_H2O, out_object, i))
    best_models_valid <- rbind(best_models_valid, eval(pred_valid, valid_H2O, out_object, i))
  }
  
  list_times  <- c(list_times, Sys.time())
  names_times <- c(names_times, paste0('The end'))
  
  time_df <- data.frame(name = names_times, timestamp = list_times)
  
  return(list(
    best_models_train = best_models_train,
    best_models_test  = best_models_test,
    best_models_valid = best_models_valid,
    time_df           = time_df
  ))
}
```

## Outcomes

### Binary classification

```{r}
out1 <- readRDS("trained_1_3_sets_3_reps_10b_10r.RData")
out2 <- readRDS("trained_4_5_sets_3_reps_10b_10r.RData")
out3 <- readRDS("trained_19_sets_3_reps_10b_10r.RData")
out4 <- readRDS("trained_25_26_sets_3_reps_10b_10r.RData")

out1$best_models_valid
out2$best_models_valid
out3$best_models_valid
out4$best_models_valid

```

```{r}
runtimes1 <- -round(out1$time_df$timestamp[1:9] - out1$time_df$timestamp[2:10])
h2o_exp1 <- h2o_experiment(out_object = out1, runtimes = runtimes1, dataset = binary_CC18[1:3], reps = 3, limit = 99999)
saveRDS(h2o_exp1, file = "h2o_1_3_sets.RData")
h2o_exp1
```

```{r}
runtimes2 <- -round(out2$time_df$timestamp[1:6] - out2$time_df$timestamp[2:7])
h2o_exp2 <- h2o_experiment(out_object = out2, runtimes = runtimes2, dataset = binary_CC18[4:5], reps = 3, limit = 99999)
saveRDS(h2o_exp2, file = "h2o_4_5_sets.RData")
h2o_exp2
```

```{r}
runtimes3 <- -round(out3$time_df$timestamp[1:3] - out3$time_df$timestamp[2:4])
h2o_exp3 <- h2o_experiment(out_object = out3, runtimes = runtimes3, dataset = binary_CC18[19], reps = 3, limit = 99999)
saveRDS(h2o_exp3, file = "h2o_19_sets.RData")
h2o_exp3
```

```{r}
runtimes4 <- -round(out4$time_df$timestamp[1:6] - out4$time_df$timestamp[2:7])
h2o_exp4 <- h2o_experiment(out_object = out4, runtimes = runtimes4, dataset = binary_CC18[25:26], reps = 3, limit = 99999)
saveRDS(h2o_exp4, file = "h2o_25_26_sets.RData")
h2o_exp4
```

### Regression

```{r}
out1 <- readRDS("trained_reg_2_3_sets_3_reps_10b_10r.RData")
out2 <- readRDS("trained_reg_5_6_sets_3_reps_10b_10r.RData")
out3 <- readRDS("trained_reg_7_8_sets_3_reps_10b_10r.RData")
out4 <- readRDS("trained_reg_4_sets_3_reps_10b_10r.RData")

out1$best_models_valid
out2$best_models_valid
out3$best_models_valid
out4$best_models_valid
```

```{r cache = TRUE, warning=FALSE}
runtimes <- -round(out1$time_df$timestamp[1:6] - out1$time_df$timestamp[2:7])
h2o_exp1 <- h2o_experiment(out_object = out1, runtimes = runtimes, dataset = regression_bench[2:3], reps = 3, limit = 99999)
saveRDS(h2o_exp1, file = "h2o_reg_2_3_sets.RData")
h2o_exp1
```

```{r cache = TRUE, warning=FALSE}
runtimes <- -round(out2$time_df$timestamp[1:6] - out2$time_df$timestamp[2:7])
h2o_exp2 <- h2o_experiment(out_object = out2, runtimes = runtimes, dataset = regression_bench[5:6], reps = 3, limit = 99999)
saveRDS(h2o_exp2, file = "h2o_reg_5_6_sets.RData")
h2o_exp2
```

```{r cache = TRUE, warning=FALSE}
runtimes <- -round(out3$time_df$timestamp[1:6] - out3$time_df$timestamp[2:7])
h2o_exp3 <- h2o_experiment(out_object = out3, runtimes = runtimes, dataset = regression_bench[7:8], reps = 3, limit = 99999)
saveRDS(h2o_exp3, file = "h2o_reg_7_8_sets.RData")
h2o_exp3
```

```{r cache = TRUE, warning=FALSE}
runtimes <- -round(out4$time_df$timestamp[1:3] - out4$time_df$timestamp[2:4])
h2o_exp4 <- h2o_experiment(out_object = out4, runtimes = runtimes, dataset = regression_bench[c(4)], reps = 3, limit = 99999)
saveRDS(h2o_exp4, file = "h2o_reg_4_sets.RData")
h2o_exp4
```

# Visualization

This code section is responsible for creating the visualizations presented in the paper.

```{r}
library(ggplot2)
library(dplyr)
library(ggbeeswarm)
library(stringr)
```

## Binary Classification

```{r}
forester_1_3   <- readRDS("trained_1_3_sets_3_reps_10b_10r.RData")
forester_4_5   <- readRDS("trained_4_5_sets_3_reps_10b_10r.RData")
forester_19    <- readRDS("trained_19_sets_3_reps_10b_10r.RData")
forester_25_26 <- readRDS("trained_25_26_sets_3_reps_10b_10r.RData")

h2o_1_3   <- readRDS("h2o_1_3_sets.RData")
h2o_4_5   <- readRDS("h2o_4_5_sets.RData")
h2o_19    <- readRDS("h2o_19_sets.RData")
h2o_25_26 <- readRDS("h2o_25_26_sets.RData")

names(h2o_4_5$best_models_valid) <- c('task_name', 'rep', 'accuracy', 'auc', 'f1')
names(h2o_19$best_models_valid) <- c('task_name', 'rep', 'accuracy', 'auc', 'f1')
names(h2o_25_26$best_models_valid) <- c('task_name', 'rep', 'accuracy', 'auc', 'f1')

names(h2o_4_5$best_models_train) <- c('task_name', 'rep', 'accuracy', 'auc', 'f1')
names(h2o_19$best_models_train) <- c('task_name', 'rep', 'accuracy', 'auc', 'f1')
names(h2o_25_26$best_models_train) <- c('task_name', 'rep', 'accuracy', 'auc', 'f1')

names(h2o_4_5$best_models_test) <- c('task_name', 'rep', 'accuracy', 'auc', 'f1')
names(h2o_19$best_models_test) <- c('task_name', 'rep', 'accuracy', 'auc', 'f1')
names(h2o_25_26$best_models_test) <- c('task_name', 'rep', 'accuracy', 'auc', 'f1')
```

```{r}
train_forester <- rbind(forester_1_3$best_models_train, forester_4_5$best_models_train, forester_19$best_models_train, forester_25_26$best_models_train)
train_forester <- train_forester[, c(8, 9, 5, 6, 7)]
train_forester$framework <- rep('forester', 24)

train_h2o <- rbind(h2o_1_3$best_models_train, h2o_4_5$best_models_train, h2o_19$best_models_train, h2o_25_26$best_models_train)
train_h2o$framework <- rep('h2o', 24)
train_performance <- rbind(train_forester, train_h2o)
train_performance

test_forester <- rbind(forester_1_3$best_models_test, forester_4_5$best_models_test, forester_19$best_models_test, forester_25_26$best_models_test)
test_forester <- test_forester[, c(8, 9, 5, 6, 7)]
test_forester$framework <- rep('forester', 24)

test_h2o <- rbind(h2o_1_3$best_models_test, h2o_4_5$best_models_test, h2o_19$best_models_test, h2o_25_26$best_models_test)
test_h2o$framework <- rep('h2o', 24)
test_performance <- rbind(test_forester, test_h2o)
test_performance

valid_forester <- rbind(forester_1_3$best_models_valid, forester_4_5$best_models_valid, forester_19$best_models_valid, forester_25_26$best_models_valid)
valid_forester <- valid_forester[, c(8, 9, 5, 6, 7)]
valid_forester$framework <- rep('forester', 24)

valid_h2o <- rbind(h2o_1_3$best_models_valid, h2o_4_5$best_models_valid, h2o_19$best_models_valid, h2o_25_26$best_models_valid)
valid_h2o$framework <- rep('h2o', 24)
valid_performance <- rbind(valid_forester, valid_h2o)
valid_performance
```

```{r}
train_performance$set <- "train"
test_performance$set <- "test"
valid_performance$set <- "valid"

df <- rbind(test_performance, train_performance, valid_performance)
df$set <- factor(df$set, levels = c("test", "valid", "train"))



df <- mutate(df, task_name_short = str_wrap(task_name, width = 8))

ggplot(data = df, aes(x = set, y = accuracy, color = framework)) + 
  geom_beeswarm(alpha = 1, size = 2) + 
  theme_minimal() + 
  labs(title = 'Performance comparison of forester and h2o',
       subtitle = 'for the binary classification task',
       x = 'Dataset',
       y = 'Accuracy',
       color = "Framework",
       shape = "Set") +
  scale_color_manual(values = c("#afc968", "#74533d", "#2aa8b2")) +
  theme(plot.title = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x = element_text(colour = 'black', size = 12),
        axis.title.y = element_text(colour = 'black', size = 12),
        axis.text.y = element_text(colour = "black", size = 6),
        axis.text.x = element_text(colour = "black", size = 9)) + 
  ylim(c(0.5, 1)) + 
  coord_flip() + 
  facet_grid(task_name_short~.,) +
  theme(strip.background = element_rect(fill = "white", color = "white"),
        strip.text = element_text(size = 6 ), 
        legend.position = "bottom",
        strip.text.y.right = element_text(angle = 0)) 

```

## Regression

```{r}
forester_reg_2_3 <- readRDS("trained_reg_2_3_sets_3_reps_10b_10r.RData")
forester_reg_4   <- readRDS("trained_reg_4_sets_3_reps_10b_10r.RData")
forester_reg_5_6 <- readRDS("trained_reg_5_6_sets_3_reps_10b_10r.RData")
forester_reg_7_8 <- readRDS("trained_reg_7_8_sets_3_reps_10b_10r.RData")

h2o_reg_2_3      <- readRDS("h2o_reg_2_3_sets.RData")
h2o_reg_4        <- readRDS("h2o_reg_4_sets.RData")
h2o_reg_5_6      <- readRDS("h2o_reg_5_6_sets.RData")
h2o_reg_7_8      <- readRDS("h2o_reg_7_8_sets.RData")

```

```{r}
train_forester <- rbind(forester_reg_2_3$best_models_train, forester_reg_4$best_models_train, forester_reg_5_6$best_models_train, forester_reg_7_8$best_models_train)
train_forester <- train_forester[, c(9, 10, 5, 6, 7, 8)]
train_forester$framework <- rep('forester', 21)

train_h2o <- rbind(h2o_reg_2_3$best_models_train, h2o_reg_4$best_models_train, h2o_reg_5_6$best_models_train, h2o_reg_7_8$best_models_train)
train_h2o$framework <- rep('h2o', 21)
train_performance <- rbind(train_forester, train_h2o)
train_performance$framework <- factor(train_performance$framework, levels = c("forester", "h2o"))
train_performance

test_forester <- rbind(forester_reg_2_3$best_models_test, forester_reg_4$best_models_test, forester_reg_5_6$best_models_test, forester_reg_7_8$best_models_test)
test_forester <- test_forester[, c(9, 10, 5, 6, 7, 8)]
test_forester$framework <- rep('forester', 21)

test_h2o <- rbind(h2o_reg_2_3$best_models_test, h2o_reg_4$best_models_test, h2o_reg_5_6$best_models_test, h2o_reg_7_8$best_models_test)
test_h2o$framework <- rep('h2o', 21)
test_performance <- rbind(test_forester, test_h2o)
test_performance$framework <- factor(test_performance$framework, levels = c("forester", "h2o"))
test_performance

valid_forester <- rbind(forester_reg_2_3$best_models_valid, forester_reg_4$best_models_valid, forester_reg_5_6$best_models_valid, forester_reg_7_8$best_models_valid)
valid_forester <- valid_forester[, c(9, 10, 5, 6, 7, 8)]
valid_forester$framework <- rep('forester', 21)

valid_h2o <- rbind(h2o_reg_2_3$best_models_valid, h2o_reg_4$best_models_valid, h2o_reg_5_6$best_models_valid, h2o_reg_7_8$best_models_valid)
valid_h2o$framework <- rep('h2o', 21)
valid_performance <- rbind(valid_forester, valid_h2o)
valid_performance$framework <- factor(valid_performance$framework, levels = c("forester", "h2o"))
valid_performance
```

```{r}
train_performance$set <- "train"
test_performance$set <- "test"
valid_performance$set <- "valid"

df <- rbind(test_performance, train_performance, valid_performance)
df$set <- factor(df$set, levels = c("test", "valid", "train"))



df <- mutate(df, task_name_short = str_wrap(task_name, width = 8))

ggplot(data = df, aes(x = set, y = rmse, color = framework)) + 
  geom_beeswarm(alpha = 1, size = 2) + 
  theme_minimal() + 
  labs(title = 'Performance comparison of forester and h2o',
       subtitle = 'for the regression task',
       x = 'Dataset',
       y = 'RMSE',
       color = "Framework",
       shape = "Set") +
  scale_color_manual(values = c("#afc968", "#74533d", "#2aa8b2")) +
  theme(plot.title = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x = element_text(colour = 'black', size = 12),
        axis.title.y = element_text(colour = 'black', size = 12),
        axis.text.y = element_text(colour = "black", size = 6),
        axis.text.x = element_text(colour = "black", size = 9)) + 
  coord_flip() + 
  facet_grid(task_name_short~., scales = 'free', space = 'free') +
  theme(strip.background = element_rect(fill = "white", color = "white"),
        strip.text = element_text(size = 6 ), 
        legend.position = "bottom",
        strip.text.y.right = element_text(angle = 0))  
```

# Raw training results

This code section is responsible for generating the data sets present in the raw_training_results and the tables present in the paper's Appendix.

```{r}
library(xlsx)
library(dplyr)
```

## Binary classification

```{r}
forester_1_3   <- readRDS("trained_1_3_sets_3_reps_10b_10r.RData")
forester_4_5   <- readRDS("trained_4_5_sets_3_reps_10b_10r.RData")
forester_19    <- readRDS("trained_19_sets_3_reps_10b_10r.RData")
forester_25_26 <- readRDS("trained_25_26_sets_3_reps_10b_10r.RData")

h2o_1_3        <- readRDS("h2o_1_3_sets.RData")
h2o_4_5        <- readRDS("h2o_4_5_sets.RData")
h2o_19         <- readRDS("h2o_19_sets.RData")
h2o_25_26      <- readRDS("h2o_25_26_sets.RData")
```

```{r}
rename_cols <- function(df) {
  names(df$best_models_valid) <- c('task_name', 'rep', 'accuracy', 'auc', 'f1')
  names(df$best_models_train) <- c('task_name', 'rep', 'accuracy', 'auc', 'f1')
  names(df$best_models_test)  <- c('task_name', 'rep', 'accuracy', 'auc', 'f1')
  return(df)
}

unify_and_merge <- function(a, b, c, d, type, col) {
  a  <- a[[col]]
  b  <- b[[col]]
  c  <- c[[col]]
  d  <- d[[col]]
  df <- rbind(a, b, c, d)
  
  if (type == 'forester') {
    df <- df[, c(8, 9, 5, 6, 7)]
  }
  df$framework <- rep(type, 24)
  
  return(df)
}

aggregate_df <- function(df) {
  df_mean <- df %>%
    group_by(task_name, framework) %>%
    summarise(mean_accuracy = mean(accuracy), mean_auc = mean(auc), mean_f1 = mean(f1))
  
  df_mean               <- data.frame(df_mean)
  df_mean$mean_accuracy <- round(df_mean$mean_accuracy, 3)
  df_mean$mean_auc      <- round(df_mean$mean_auc , 3)
  df_mean$mean_f1       <- round(df_mean$mean_f1, 3)
  df <- df_mean
  
  return(df)
}
```

```{r}
h2o_1_3        <- rename_cols(h2o_1_3)
h2o_4_5        <- rename_cols(h2o_4_5)
h2o_19         <- rename_cols(h2o_19)
h2o_25_26      <- rename_cols(h2o_25_26)

forester_train <- unify_and_merge(forester_1_3, forester_4_5, forester_19, forester_25_26, 'forester', 1)
forester_test  <- unify_and_merge(forester_1_3, forester_4_5, forester_19, forester_25_26, 'forester', 2)
forester_valid <- unify_and_merge(forester_1_3, forester_4_5, forester_19, forester_25_26, 'forester', 3)

h2o_train      <- unify_and_merge(h2o_1_3, h2o_4_5, h2o_19, h2o_25_26, 'h2o', 1)
h2o_test       <- unify_and_merge(h2o_1_3, h2o_4_5, h2o_19, h2o_25_26, 'h2o', 2)
h2o_valid      <- unify_and_merge(h2o_1_3, h2o_4_5, h2o_19, h2o_25_26, 'h2o', 3)

train          <- rbind(forester_train, h2o_train)
test           <- rbind(forester_test, h2o_test)
valid          <- rbind(forester_valid, h2o_valid)

train_mean     <- aggregate_df(train)
test_mean      <- aggregate_df(test)
valid_mean     <- aggregate_df(valid)
```

```{r}
write.xlsx(train_mean, "train_mean.xlsx", row.names = FALSE)
write.xlsx(test_mean, "test_mean.xlsx", row.names = FALSE)
write.xlsx(valid_mean, "valid_mean.xlsx", row.names = FALSE)

write.csv(train_mean, "train_mean.csv", row.names = FALSE)
write.csv(test_mean, "test_mean.csv", row.names = FALSE)
write.csv(valid_mean, "valid_mean.csv", row.names = FALSE)

write.xlsx(train, "train.xlsx", row.names = FALSE)
write.xlsx(test, "test.xlsx", row.names = FALSE)
write.xlsx(valid, "valid.xlsx", row.names = FALSE)

write.csv(train, "train.csv", row.names = FALSE)
write.csv(test, "test.csv", row.names = FALSE)
write.csv(valid, "valid.csv", row.names = FALSE)
```

## Regression

```{r}
forester_reg_2_3 <- readRDS("trained_reg_2_3_sets_3_reps_10b_10r.RData")
forester_reg_4   <- readRDS("trained_reg_4_sets_3_reps_10b_10r.RData")
forester_reg_5_6 <- readRDS("trained_reg_5_6_sets_3_reps_10b_10r.RData")
forester_reg_7_8 <- readRDS("trained_reg_7_8_sets_3_reps_10b_10r.RData")

h2o_reg_2_3      <- readRDS("h2o_reg_2_3_sets.RData")
h2o_reg_4        <- readRDS("h2o_reg_4_sets.RData")
h2o_reg_5_6      <- readRDS("h2o_reg_5_6_sets.RData")
h2o_reg_7_8      <- readRDS("h2o_reg_7_8_sets.RData")
```

```{r}
rename_cols <- function(df) {
  names(df$best_models_valid) <- c('task_name', 'rep', 'rmse', 'mse', 'r2', 'mae')
  names(df$best_models_train) <- c('task_name', 'rep', 'rmse', 'mse', 'r2', 'mae')
  names(df$best_models_test)  <- c('task_name', 'rep', 'rmse', 'mse', 'r2', 'mae')
  return(df)
}

unify_and_merge <- function(a, b, c, d, type, col) {
  a  <- a[[col]]
  b  <- b[[col]]
  c  <- c[[col]]
  d  <- d[[col]]
  df <- rbind(a, b, c, d)
  
  if (type == 'forester') {
    df <- df[, c(9, 10, 5, 6, 7, 8)]
  }
  df$framework <- rep(type, 21)
  
  return(df)
}

aggregate_df <- function(df) {
  df_mean <- df %>%
    group_by(task_name, framework) %>%
    summarise(mean_rmse = mean(rmse), mean_mse = mean(mse), mean_r2 = mean(r2), mean_mae = mean(mae))
  
  df_mean               <- data.frame(df_mean)
  df_mean$mean_rmse     <- round(df_mean$mean_rmse, 3)
  df_mean$mean_mse      <- round(df_mean$mean_mse , 3)
  df_mean$mean_r2       <- round(df_mean$mean_r2, 3)
  df_mean$mean_mae      <- round(df_mean$mean_mae, 3)
  df <- df_mean
  
  return(df)
}
```

```{r}
h2o_reg_2_3     <- rename_cols(h2o_reg_2_3)
h2o_reg_4        <- rename_cols(h2o_reg_4)
h2o_reg_5_6      <- rename_cols(h2o_reg_5_6)
h2o_reg_7_8      <- rename_cols(h2o_reg_7_8)

forester_train <- unify_and_merge(forester_reg_2_3, forester_reg_4, forester_reg_5_6, forester_reg_7_8, 'forester', 1)
forester_test  <- unify_and_merge(forester_reg_2_3, forester_reg_4, forester_reg_5_6, forester_reg_7_8, 'forester', 2)
forester_valid <- unify_and_merge(forester_reg_2_3, forester_reg_4, forester_reg_5_6, forester_reg_7_8, 'forester', 3)

h2o_train      <- unify_and_merge(h2o_reg_2_3, h2o_reg_4, h2o_reg_5_6, h2o_reg_7_8, 'h2o', 1)
h2o_test       <- unify_and_merge(h2o_reg_2_3, h2o_reg_4, h2o_reg_5_6, h2o_reg_7_8, 'h2o', 2)
h2o_valid      <- unify_and_merge(h2o_reg_2_3, h2o_reg_4, h2o_reg_5_6, h2o_reg_7_8, 'h2o', 3)

train          <- rbind(forester_train, h2o_train)
test           <- rbind(forester_test, h2o_test)
valid          <- rbind(forester_valid, h2o_valid)

train_mean     <- aggregate_df(train)
test_mean      <- aggregate_df(test)
valid_mean     <- aggregate_df(valid)
```

```{r}
write.xlsx(train_mean, "train_mean_reg.xlsx", row.names = FALSE)
write.xlsx(test_mean, "test_mean_reg.xlsx", row.names = FALSE)
write.xlsx(valid_mean, "valid_mean_reg.xlsx", row.names = FALSE)

write.csv(train_mean, "train_mean_reg.csv", row.names = FALSE)
write.csv(test_mean, "test_mean_reg.csv", row.names = FALSE)
write.csv(valid_mean, "valid_mean_reg.csv", row.names = FALSE)

write.xlsx(train, "train_reg.xlsx", row.names = FALSE)
write.xlsx(test, "test_reg.xlsx", row.names = FALSE)
write.xlsx(valid, "valid_reg.xlsx", row.names = FALSE)

write.csv(train, "train_reg.csv", row.names = FALSE)
write.csv(test, "test_reg.csv", row.names = FALSE)
write.csv(valid, "valid_reg.csv", row.names = FALSE)
```

# Calculation time analysis

During the conduction of h2o experiments, it occurred to us, that although we've set the same amount of time for every single task for the h2o as the forester had, the h2o AutoML method lasted much longer than it should. To briefly explore this issue, we've decided to analyse the times needed for every experiment for both frameworks. The results show that despite setting exactly the same time for h2o to run for every experiment, this framework calculates this time in an unknown way, as our empirical results show that the h2o runs lasted two times longer than the forester on average.

## Binary classification

```{r}
forester_1_3   <- readRDS("trained_1_3_sets_3_reps_10b_10r.RData")
forester_4_5   <- readRDS("trained_4_5_sets_3_reps_10b_10r.RData")
forester_19    <- readRDS("trained_19_sets_3_reps_10b_10r.RData")
forester_25_26 <- readRDS("trained_25_26_sets_3_reps_10b_10r.RData")

h2o_1_3   <- readRDS("h2o_1_3_sets.RData")
h2o_4_5   <- readRDS("h2o_4_5_sets.RData")
h2o_19    <- readRDS("h2o_19_sets.RData")
h2o_25_26 <- readRDS("h2o_25_26_sets.RData")
```

```{r}
create_time_df <- function(forester, h2o) {
  time_df <- list()
  task_name <- c()
  for (i in 1:(length(forester$time_df$name) -1)) {
    task_name <- c(task_name, strsplit(forester$time_df$name[1:(nrow(forester$time_df) - 1)][i], split = ' ')[[1]][2])
  }
  time_df$task_name      <- task_name
  time_df$forester_time  <- round(forester$time_df$timestamp[2:(nrow(forester$time_df))] - 
                                  forester$time_df$timestamp[1:(nrow(forester$time_df) - 1)])
  time_df$h2o_time       <- round(h2o$time_df$timestamp[2:(nrow(h2o$time_df))] - h2o$time_df$timestamp[1:(nrow(h2o$time_df) - 1)])
  time_df$difference     <- time_df$forester_time - time_df$h2o_time
  time_df$relative_diff   <- time_df$forester_time/time_df$h2o_time
  return(data.frame(time_df))
}

aggregate_times <- function(df) {
  df_mean <- df %>%
    group_by(task_name) %>%
    summarise(mean_forester_time = mean(forester_time), mean_h2o_time = mean(h2o_time), 
              mean_difference = mean(difference), mean_relative_diff = mean(relative_diff))
  
  df_mean               <- data.frame(df_mean)
  df_mean$mean_forester_time     <- round(df_mean$mean_forester_time, 2)
  df_mean$mean_h2o_time          <- round(df_mean$mean_h2o_time , 2)
  df_mean$mean_difference        <- round(df_mean$mean_difference, 2)
  df_mean$mean_relative_diff     <- round(df_mean$mean_relative_diff, 2)
  df <- df_mean
  
  return(df)
}
```

```{r}
time_df_binary_clf <- rbind(create_time_df(forester_1_3, h2o_1_3), 
                            create_time_df(forester_4_5, h2o_4_5),
                            create_time_df(forester_19, h2o_19),
                            create_time_df(forester_25_26, h2o_25_26))

mean_time_df_binary_clf <- aggregate_times(time_df_binary_clf)
mean_time_df_binary_clf

```

```{r}
write.xlsx(time_df_binary_clf, "time_df_binary_clf.xlsx", row.names = FALSE)
write.csv(time_df_binary_clf, "time_df_binary_clf.csv", row.names = FALSE)

write.xlsx(mean_time_df_binary_clf, "mean_time_df_binary_clf.xlsx", row.names = FALSE)
write.csv(mean_time_df_binary_clf, "mean_time_df_binary_clf.csv", row.names = FALSE)
```

## Regression

```{r}
forester_reg_2_3 <- readRDS("trained_reg_2_3_sets_3_reps_10b_10r.RData")
forester_reg_4   <- readRDS("trained_reg_4_sets_3_reps_10b_10r.RData")
forester_reg_5_6 <- readRDS("trained_reg_5_6_sets_3_reps_10b_10r.RData")
forester_reg_7_8 <- readRDS("trained_reg_7_8_sets_3_reps_10b_10r.RData")

h2o_reg_2_3      <- readRDS("h2o_reg_2_3_sets.RData")
h2o_reg_4        <- readRDS("h2o_reg_4_sets.RData")
h2o_reg_5_6      <- readRDS("h2o_reg_5_6_sets.RData")
h2o_reg_7_8      <- readRDS("h2o_reg_7_8_sets.RData")
```

```{r}
time_df_regression <- rbind(create_time_df(forester_reg_2_3, h2o_reg_2_3), 
                            create_time_df(forester_reg_4, h2o_reg_4),
                            create_time_df(forester_reg_5_6, h2o_reg_5_6),
                            create_time_df(forester_reg_7_8, h2o_reg_7_8))
mean_time_df_regression <- aggregate_times(time_df_regression)
mean_time_df_regression
```

```{r}
write.xlsx(time_df_regression, "time_df_regression.xlsx", row.names = FALSE)
write.csv(time_df_regression, "time_df_regression.csv", row.names = FALSE)

write.xlsx(mean_time_df_regression, "mean_time_df_regression.xlsx", row.names = FALSE)
write.csv(mean_time_df_regression, "mean_time_df_regression.csv", row.names = FALSE)
```
