---
title: "AutoML Framework Comparison"
author: "Hubert Ruczyński"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

In this document we will compare the major AutoML workflows in R with
the `forester` package from the user perspective, focusing mostly on the
features provided by the package, their methodology and the convenience
of use. The aforementioned workflows are: `H2O`, and `mlr3` with
`mlr3automl`.

# Installation and set up

## forester

The forester package is not yet on CRAN, but the installation of the
core functions is really simple. However to use the package properly,
the authors advise installation of additional packages which are not on
CRAN (`catboost`, `ggradar`, `tinytex`). All instructions are present on
the GitHub repository and are easy to find.

```{r forester main, eval=FALSE}
# required
install.packages("devtools")
devtools::install_github("ModelOriented/forester")

# optional - not on CRAN
install.packages("devtools")
devtools::install_url('https://github.com/catboost/catboost/releases/download/v1.1.1/catboost-R-Darwin-1.1.1.tgz', INSTALL_opts = c("--no-multiarch", "--no-test-load", "--no-staged-install"))
devtools::install_github('ricardo-bion/ggradar', dependencies = TRUE)
install.packages('tinytex')
tinytex::install_tinytex()
```

The set up of the package after the installation is also simple and
clean.

```{r forester setup}
library(forester)
```

## H2O

The installation of `H2O` is simple if we want tot grab, a delayed CRAN
version, and a bit harder when it comes to the most recent version. The
CRAN installation is announced at GitHub page, whereas the alternative
can be found on the documentation page. Moreover `H2O` always requires
`Java` to work, so the user has to install it too.

```{r H2O installation, eval=FALSE}
# CRAN installation
install.packages("h2o")

# Alternative installation
if ("package:h2o" %in% search()) { detach("package:h2o", unload = TRUE) }
if ("h2o" %in% rownames(installed.packages())) { remove.packages("h2o") }
pkgs <- c("RCurl","jsonlite")
for (pkg in pkgs) {
  if (! (pkg %in% rownames(installed.packages()))) { install.packages(pkg) }
}
install.packages("h2o", type = "source", repos = (c("http://h2o-release.s3.amazonaws.com/h2o/latest_stable_R")))
```

To run `H2O` package we not only need to import the package, but also
initialize an `H2O` environment. This step is not hard, however it takes
some time and when the user wants to interrupt code execution it will
also terminate whole environment which makes him initialized it again.

```{r H2O setup}
library(h2o)
localH2O = h2o.init()
```

## mlr3

The main problem with `mlr3` as an AutoML package is that, it is not
initially AutoML. To call `mlr3` an AutoML we have to install another
package called `mlr3automl`, which comes from a different developers
than the original one. Working with `mlr3` is tiresome, because the
framework has dozens of subpackages that add some features. Luckily the
user doesn't have to install all of them one by one, because one can
install just `mlr3verse`, but all subpackages have to be imported one by
one.

```{r mlr3 main, eval=FALSE}
install.packages("devtools")
install.packages("mlr3verse")
devtools::install_github('https://github.com/mlr-org/mlr3extralearners')
devtools::install_github('https://github.com/a-hanf/mlr3automl', dependencies = TRUE)
```

```{r mlr3 setup, message=FALSE}
# required
library(mlr3verse)
library(mlr3automl)
# optional
library(mlr3viz)
library(mlr3tuning) 
library(mlr3learners) 
library(mlr3pipelines)
```

# Preprocessing

## forester

The `forester` package preprocessing methods are integrated within the
`train()` function and consists of multiple different functions, which
are: `preprocessing()`, `train_test_balance()`, and `prepare_data()`.
The first function gets rid of poor quality information like removing
static columns, imputing missing values with MICE algorithm and
binarizes the target for binary classification task. The method has also
alternative mode called `advanced_preprocessing`, where we perform
additional steps like removing correlated values, id columns and perform
BORUTA selection of most important columns. The second one splits the
initial data set into the train, test and validation subsets with
proportions provided by the user. The method used for the partitioning
ensures that the subsets will be balanced in terms of labels or
distributions. The last function prepares the data frames to be in a
form required by the specific models, which for example means that for
xgboost model we have to provide one hot encoded categorical values.

```{r forester preprocessing }
data('lisbon')
prep_data <- preprocessing(lisbon, 'Price',advanced = FALSE, verbose = TRUE)
print(head(prep_data$data))

prep_data2 <- preprocessing(lisbon, 'Price',advanced = TRUE, verbose = TRUE)
print(head(prep_data2$data))

split <- train_test_balance(prep_data$data, 'Price', balance = TRUE, 'regression',
                            fractions = c(0.6, 0.2, 0.2))
print(head(split$train))
print(head(split$test))


engine = c('ranger', 'xgboost', 'decision_tree')
train_data <- prepare_data(split$train, 'Price', engine)
test_data  <- prepare_data(split$test, 'Price', engine, predict = TRUE, split$train)

print(head(train_data$xgboost_data))
print(head(test_data$ranger_data))
```

## H2O

The `H2O` AutoML solutions preprocessing is really poor and lack plenty
of important features. The authors have the preprocessing in mind
however the only options available so far are the target encoding and
balancing the classes for train, test split. The user however has to
split the data set on his own, before running the AutoML function.

## mlr3

In case of `mlr3` the preprocessing exists and the authors claim that
their preprocessing is versatile, because they tested it on 39
challenging data sets in the `AutoML Benchmark`. On the other hand, we
can see that the preprocessing itself is not automated and it is the
user who has to design whole process. The basic prepossessing method
used in the workflow is the automatic train test split. The
preprocessing can also be set inside of the `AutoML()` function and it
uses Imputation, Impact Encoding and PCA.

```{r mlr3 preprocessing }
imbalanced_preproc = po("imputemean") %>>%
  po("smote") %>>%
  po("classweights", minor_weight = 2)

automl_model = AutoML(task = tsk("pima"),
  preprocessing = imbalanced_preproc) 
```

# AutoML

## forester

The `forester` AutoML pipeline is hidden inside a single `train()`
function, which covers all of the smaller ML pipelines like data
preprocessing model tuning, evaluation. It means that the users
interaction and preparations before using the package are absolutely
minimal. The authors keep their tool simple to use in order to set the
low level of entry for using the package. The `train()` function however
has plenty of parameters which enable the user to interact and model the
training process.

The most important and basic outcome from the train is the ranked list
in form of the `score_test` or `score_valid`, depending won which data
set do we want to evaluate the models. This objects lets us compare the
models in terms of multiple metric values.

The ranked lists are only a fraction of the output given by the
function. The return objects contains all the spitted data sets, columns
removed by the preprocessing, all predictions, models, metric values,
used engines, data check report and much more.

The engines available for both tasks are: `ranger`, `xgboost`,
`decision tree`, `lighgbm`, and `catboost`.

```{r forester AutoML}
library(forester)
data('lisbon')
train_output <- train(lisbon, 'Price', verbose = TRUE, 
                      train_test_split = c(0.6, 0.2, 0.2), bayes_iter = 10, 
                      random_evals = 3, advanced_preprocessing = FALSE)
train_output$score_test
```

## H2O

The `H2O` AutoML is limited to 6 models with additional 2 stacked
ensembles, which are: `DRF` (Distributed Random Forest), `XRT`
(Extremely Randomized Trees), `GLM` (Generalized Linear Model with
regularization), `XGBoost` (XGBoost GBM), `GBM` (H2O GBM),
`DeepLearning` (Fully-connected multi-layer artificial neural network)
and `Full ensemble` with `Subset ensemble`.

The authors claim that the only needed arguments are `y` which stands
for the target column name and `training_frame` which is the data set,
however, to actually own these the user has to prepare the split and
correct format of the data frame by himself. One of the most interesting
options is the setting the full time of the computation, however in
reality the training process takes much more time than the one specified
by the `max_runtime_secs` parameter.

The main function provides a load of additional functionalities such as
setting a seed, the choice of sorting metric, ability to choose the ML
engines or the level of verbosity.

The results representation as a leaderboard is really clear, however the
names of the models are sometimes foggy. The possibilities to get the
best model predictions and evaluation are also pretty simple. All the
objects returned by the `h2o.automl` function are: `leader`,
`leaderboard`, `event_log`, and training `training_info`. However with
the usage of additional functions the user is able to obtain: specific
model details by its id, prediction of the model, the best model of the
given algorithm, the parameters of the model or its metrics.

It is also worth noticing, that there are no preprocessing functions
included inside the main AutoML workflow which makes using it more
complex. Moreover the output of the function is not entirely complete
and the user has to find other function from the package (where there
are lots of them, because whole H2O is huge) to get basic info.

```{r H2O AutoML}
h2o.init()
# split from the forester
split <- train_test_balance(lisbon, 'Price', balance = TRUE, 'regression',
                            fractions = c(0.6, 0.2, 0.2)) 
train_H2O <- as.h2o(split$train)
test_H2O  <- as.h2o(split$test)

y <- "Price"
x <- setdiff(names(train_H2O), y)

aml <- h2o.automl(x = x, y = y,
                  training_frame = train_H2O,
                  max_runtime_secs = 90,
                  seed = 1)

aml@leaderboard
```

```{r H2O AutoML - preds}
pred <- h2o.predict(aml, test_H2O)
print(pred)

perf <- h2o.performance(aml@leader, test_H2O)
print(perf)
```

## mlr3

The `mlr3` AutoML comes from the independent developer than the original
package and is available through `mlr3automl` package. The method is
fully compatible with the main package, which means that it operates in
a similar way with the usage of learners, tasks, preprocessing, and so
on. Default available engines are: `ranger`, `xgboost`, `liblinear` for
both binary classification and regression, and for regression only the
`svm` and `cv_glmnet`. The user can also provide other models, but the
authors claim that in some cases it might not work properly. Similarly
to the `H2O` package, we can define a time spent on the learning process
with `learner_timeout` and `runtime` parameters. The user is also able
to provide preprocessing methods created with `mlr3`, via `preprocesing`
parameter.

One of the major inconveniences is the necessity to make predictions on
our own, instead of getting clean results. It is also unclear how to
compare the trained models with each other to chose the best one.
Moreover there are no built-in method for metrics calculation. The user
interface is absolutely unclear and inconvenient.

```{r mlr3 AutoML}
iris_task     = tsk("iris")
iris_model    = AutoML(iris_task, preprocessing = imbalanced_preproc)
train_indices = sample(1:iris_task$nrow, 2/3*iris_task$nrow)

iris_model$train(row_ids = train_indices)

predict_indices = setdiff(1:iris_task$nrow, train_indices)
predictions     = iris_model$predict(row_ids = predict_indices)
print(predictions)
```

# Feature selection

## forester

In the `forester` package the feature selection can be done in one of
the two ways. The first one, which takes place during the advanced
preprocessing method is running a `BORUTA` selection algorithm, whereas
the second option is to create an explainer and calculate the Feature
Importance plots. The second option however makes no impact during the
training process, because it is done after the models creation. The
given information however, could encourage the user to delete less
important columns by himself before the second training attempt.

## H2O

The `H2O` doesn't support feature selection.

## mlr3

In the `mlr3automl` there is no option of providing any kind of feature
selection. We can only stretch the definition that running a PCA during
the preprocessing can be counted as a feature selection, but it is far
from being a proper method.

# Model tuning

## forester

In the `forester` package, the model tuning consists of 3 major
workflows: model training with `basic parameters`, training with
`random search` on a specified grid, and the `Bayesian Optimization`
method. The first option is a reasonable, baseline set of parameters,
because they are not randomly selected and the algorithms authors chose
them, because they are generally good. The second options purpose is to
possibly search a hyperparameter space for a more promising starting
point. The most important tuning method is the `Bayesian Optimiztation`,
because it runs a optimization method that searches for the local
optimum, by exploring the surroundings of the best found point. The
method results in the best models creation, however is also time
consuming.

## H2O

The `H2O` model tuning is focused around the hyperparameter gird search
run on all of the engines which are: `DRF` (Distributed Random Forest),
`XRT` (Extremely Randomized Trees), `GLM` (Generalized Linear Model with
regularization), `XGBoost` (XGBoost GBM) and `GBM` (H2O GBM). The user
has no option to define the searching space. After training the models
(the amount of trained models depends on the `max_models` or
`max_runtime_secs` parameters), the algorithm creates two ensembles: the
first one contains all the models, whereas the second one a subset of
them, so two ensembles are added in total.

## mlr3

There model tuning in `mlr3automl` starts from evaluating 8 fixed
hyperparameter configuration that proved to be good staring points and
later it continues the training with a `mlr3hyperband` optimization
which is a multi-fidelity approach that speeds up the random search.

# Visualization

## forester

The visualization from the `forester` are mainly connected to the
explainability of the models and are described in `Explanation` and
`Report` sections of the document. The plots or of high meritocratic
quality, and have consistent and overthought layout.

## H2O

The visualization from the `H2O` are mainly connected to the
explainability of the models and are described in `Explanation` and
`Report` sections of the document. The plots or of high meritocratic
quality, however their visual level is pretty poor.

## mlr3

The visualizations for `mlr3` are provided via the `mlr3viz` package and
the `autoplot` method. It provides an object specific plot that renders
automatically, depending on the type of the given object. The
visualizations are however of quiet poor quality and are really shallow.

# Explanation

## forester

The `forester` package is the part of Model Oriented universe created by
the MI2 Data Lab, and that's why the authors decided to use one of the
best packages implementing XAI methods, which is `DALEX`. The `forester`
implements an `explain()` function, which creates a `DALEX` explainer,
which saves the users time with the most time-consuming process. The
explainer can be later used by original functions from the XAI package,
for example to create Feature Importance plot.

```{r}
library(DALEX)
exp_list <- forester::explain(models = train_output$best_models[[1]],
               test_data = train_output$test_data,
               y = train_output$y)
exp <- exp_list$xgboost_bayes
p1 <- DALEX::model_parts(exp)
plot(p1)
```

## H2O

The `H2O` package implements their own explanation functions via the
`h2o.explain()` function which can be called for a single model and for
the whole aml object. The second case will be mentioned in the report
section.

For the single model, the user can obtain plenty of XAI plots, such as
Residual Analysis, Variable Importance, Partial Dependence, and
Individual Conditional Expectations. Every visualization comes with the
contextual description of what happens on the plot.

```{r}
model <- aml@leader
exm   <- h2o.explain(model, test_H2O)
exm

```

## mlr3

The `mlr3automl` package is compatible with two major XAI workflows
which are `DALEX` and `iml` and provides tools to easily use their
functionalities on the outcomes.

```{r}
library(DALEXtra)
dalex_explainer = iris_model$explain(iml_package = "DALEX")
iml_explainer = iris_model$explain(iml_package = "iml")

# compute and plot feature permutation importance using DALEX
dalex_importance = DALEX::model_parts(dalex_explainer)
plot(dalex_importance)

# partial dependency plot using iml package
iml_pdp = iml::FeatureEffect$new(iml_explainer, feature = "Sepal.Width", method = "pdp")
plot(iml_pdp)
```

# Report

## forester

The `forester` package implements two forms of the reports. The first
and less complex one is the data check report implemented as
`check_data()` function. This lightweight report informs the user about
the quality of the used data set. It points out the problems with the
data set informing about missing values, duplicated columns or highly
correlated features.

```{r}
check_data(lisbon, 'Price')
```

The second and more complex form of the report is obtained via the
`report()` function, which creates a report depending on the type of the
ML task, which includes the ranked list, plots comparing the best
models, plots describing the best model, XAI plots and the data check
report.

```{r}
report(train_output, 'report.pdf')
```

## H2O

The `H2O` package indirectly implements kind of the report which is
obtained by the `h2o.explain()` function called on the aml object. In
this case, the output of the function is not only XAI specific and it is
delivered as a form of report that includes: the leaderboard, Residual
Analysis plot, Variable Importance plot and Heatmap, Model Correlation
Heatmap and SHAP Summary.

```{r}
# Explain an AutoML object
exa <- h2o.explain(aml, test_H2O)
exa
```

## mlr3

The `mlr` doesn't have any form of training summarization and reporting.

# Workflow comparison

This section compares the amount of code needed to go through all the
pipelines elements and use the most important features for AutoML.

## forester

```{r forester summary, eval=FALSE}
# needed
install.packages("devtools")
devtools::install_github("ModelOriented/forester")
# optional
install.packages("devtools")
devtools::install_url('https://github.com/catboost/catboost/releases/download/v1.1.1/catboost-R-Darwin-1.1.1.tgz', INSTALL_opts = c("--no-multiarch", "--no-test-load", "--no-staged-install"))
devtools::install_github('ricardo-bion/ggradar', dependencies = TRUE)
install.packages('tinytex')
tinytex::install_tinytex()
# AutoML
library(forester)
data('lisbon')
train_output <- train(lisbon, 'Price', verbose = TRUE, 
                      train_test_split = c(0.6, 0.2, 0.2), bayes_iter = 10, 
                      random_evals = 3, advanced_preprocessing = FALSE)
train_output$score_test
# explanation
library(DALEX)
exp <- forester::explain(models = train_output$best_models[[1]],
               test_data = train_output$test_data,
               y = train_output$y)
exp <- exp_list$xgboost_bayes
p1 <- DALEX::model_parts(exp)
plot(p1)
# reporting, visualization
report(train_output, 'report.pdf')
```

## H2O

```{r}
install.packages("h2o")

# Alternative installation (most common)
if ("package:h2o" %in% search()) { detach("package:h2o", unload = TRUE) }
if ("h2o" %in% rownames(installed.packages())) { remove.packages("h2o") }
pkgs <- c("RCurl","jsonlite")
for (pkg in pkgs) {
  if (! (pkg %in% rownames(installed.packages()))) { install.packages(pkg) }
}
install.packages("h2o", type = "source", repos = (c("http://h2o-release.s3.amazonaws.com/h2o/latest_stable_R")))

# AutoML
library(h2o)
h2o.init()
# split from the forester, H2O has none
split <- train_test_balance(lisbon, 'Price', balance = TRUE, 'regression',
                            fractions = c(0.6, 0.2, 0.2)) 
train_H2O <- as.h2o(split$train)
test_H2O  <- as.h2o(split$test)

y <- "Price"
x <- setdiff(names(train_H2O), y)

aml <- h2o.automl(x = x, y = y,
                  training_frame = train_H2O,
                  max_runtime_secs = 90,
                  seed = 1)

aml@leaderboard

pred <- h2o.predict(aml, test_H2O)
print(pred)

perf <- h2o.performance(aml@leader, test_H2O)
print(perf)
# Explain an AutoML model
model <- aml@leader
exm   <- h2o.explain(model, test_H2O)
exm

# Explain an AutoML object
exa <- h2o.explain(aml, test_H2O)
exa
```

## mlr3

```{r}
install.packages("devtools")
install.packages("mlr3verse")
devtools::install_github('https://github.com/mlr-org/mlr3extralearners')
devtools::install_github('https://github.com/a-hanf/mlr3automl', dependencies = TRUE)
# required
library(mlr3verse)
library(mlr3automl)
# optional
library(mlr3viz)
library(mlr3tuning) 
library(mlr3learners) 
library(mlr3pipelines)

imbalanced_preproc = po("imputemean") %>>%
  po("smote") %>>%
  po("classweights", minor_weight = 2)


iris_task     = tsk("iris")
iris_model    = AutoML(iris_task, preprocessing = imbalanced_preproc)
train_indices = sample(1:iris_task$nrow, 2/3*iris_task$nrow)

iris_model$train(row_ids = train_indices)

predict_indices = setdiff(1:iris_task$nrow, train_indices)
predictions     = iris_model$predict(row_ids = predict_indices)
print(predictions)

library(DALEXtra)
dalex_explainer = iris_model$explain(iml_package = "DALEX")
iml_explainer = iris_model$explain(iml_package = "iml")

# compute and plot feature permutation importance using DALEX
dalex_importance = DALEX::model_parts(dalex_explainer)
plot(dalex_importance)

# partial dependency plot using iml package
iml_pdp = iml::FeatureEffect$new(iml_explainer, feature = "Sepal.Width", method = "pdp")
plot(iml_pdp)
```

# Documentation

## forester

Package is small, and the vignettes and documentation is small, clear,
and understandable.

## H2O

Package is huge, has vast, detailed documentation for the AutoML part
and is of really high quality, but delving into more advanced features
is hard due to the abundance of documentation pages.

## mlr3

The documentation is incomplete, lacks the advanced examples, fining
what you need is hard.
