---
title: "Survival analysis demo"
author: "Hubert Ruczyński"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    theme: lumen
    toc_depth: 3
    number_sections: yes
    latex_engine: xelatex
---

```{css, echo=FALSE}
body .main-container {
  max-width: 1820px !important;
  width: 1820px !important;
}
body {
  max-width: 1820px !important;
  width: 1820px !important;
  font-family: Helvetica !important;
  font-size: 16pt !important;
}
h1,h2,h3,h4,h5,h6{
  font-size: 24pt !important;
}
```

# Downloads

The necessary downloads required for the forester package to work properly, if downloaded, the user can skip this part.

```{r eval = FALSE}
install.packages("devtools")
devtools::install_github("ModelOriented/forester")
devtools::install_github('catboost/catboost', subdir = 'catboost/R-package')
devtools::install_github('ricardo-bion/ggradar', dependencies = TRUE)
install.packages('tinytex')
tinytex::install_tinytex()
```

# Imports

Importing the forester library handles everything for us.

```{r warning = FALSE, message = FALSE}
library(forester)
```

# Train

In the beginning we import a survival analysis task called peakV02, and later proceed with the forester training. Let's notice that this time we don't provide any y value, as the task is described by the pair `ttodead`, and `died`. The first step is the description of our dataset, which outlines multiple issues with the dataset, even though the `forester` successfully prepares the results.

```{r}
data(peakVO2, package = 'randomForestSRC')
results <- train(
  data             = peakVO2,
  y                = NULL,
  time             = 'ttodead',
  status           = 'died',
  type             = 'auto',
  verbose          = TRUE,
  train_test_split = c(0.6, 0.2, 0.2),
  split_seed       = NULL,
  bayes_iter       = 10,
  random_evals     = 10,
  metrics          = 'auto',
  sort_by          = 'auto'
)
```

# Results

Finally we can see the results presented as a ranked list of evaluated models. The models are compared with the Brier Score (the smaller the better), and Concordance Index (the bigger the better).

```{r}
results$score_test
```

```{r}
results$score_valid
```
