<<<<<<< HEAD
---
title: "Ablation study of forester: Datasets Information"
author: "Hubert Ruczyński"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    theme: lumen
    toc_depth: 3
    number_sections: yes
    latex_engine: xelatex
---

```{css, echo=FALSE}
body .main-container {
  max-width: 1820px !important;
  width: 1820px !important;
}
body {
  max-width: 1820px !important;
  width: 1820px !important;
  font-family: Helvetica !important;
  font-size: 16pt !important;
}
h1,h2,h3,h4,h5,h6{
  font-size: 24pt !important;
}
```

# Downloads

The necessary downloads required for the forester package to work properly, if downloaded, the user can skip this part.

```{r eval = FALSE}
install.packages("devtools")
devtools::install_github("ModelOriented/forester")
devtools::install_github('catboost/catboost', subdir = 'catboost/R-package')
devtools::install_github('ricardo-bion/ggradar', dependencies = TRUE)
install.packages('tinytex')
tinytex::install_tinytex()
```

# Imports

Importing the necessary libraries.

```{r warning=FALSE, message=FALSE}
library(forester)
library(farff)
```

# Datasets analysis

In this section we will describe the datasets with the usage of `data_check()` function from the forester package.

## Binary classification

```{r}
binary_CC18 <- readRDS("binary_CC18.RData")
binary_CC18 <- binary_CC18[c(1, 2, 3, 4, 5, 19, 25, 26)]
```

### Data Check

#### kr-vs-kp

```{r}
s <- check_data(binary_CC18$`kr-vs-kp`, 'class')
```

#### breast-w

```{r}
s <- check_data(binary_CC18$`breast-w`, 'Class')
```

#### credit-approval

```{r}
s <- check_data(binary_CC18$`credit-approval`, 'class')
```

#### credit-g

```{r}
s <- check_data(binary_CC18$`credit-g`, 'class')
```

#### diabetes

```{r}
s <- check_data(binary_CC18$diabetes, 'class')
```

#### phoneme

```{r}
s <- check_data(binary_CC18$phoneme, 'Class')
```

#### banknote-authentication

```{r}
s <- check_data(binary_CC18$`banknote-authentication`, 'Class')
```

#### blood-transfusion-service-center

```{r}
s <- check_data(binary_CC18$`blood-transfusion-service-center`, 'Class')
```

## Regression

Loading widely used datasets from OpenML. If you are reproducing the paper step by step, skip this one, as we will load a specially prepared version in another cell.

```{r warning=FALSE, message=FALSE, eval=FALSE}
wind              <- readARFF('regression_datasets/wind.arff') # Not regression task
communities_crime <- readARFF('regression_datasets/phpeZQVCe.arff') # ViolentCrimesPerPop
bank32nh          <- readARFF('regression_datasets/phpYYZ4Qc.arff') # Target: rej
wine_quality      <- readARFF('regression_datasets/wine_quality.arff') # Target: quality
Mercedes_Benz     <- readARFF('regression_datasets/dataset.arff') # Target: y (2nd col)
Mercedes_Benz_y   <- Mercedes_Benz$y
Mercedes_Benz     <- Mercedes_Benz[, -2]
Mercedes_Benz$y   <- Mercedes_Benz_y # the last one
kin8nm            <- readARFF('regression_datasets/dataset_2175_kin8nm.arff') # Target: y
pol               <- readARFF('regression_datasets/dataset_2187_pol.arff') # Target: foo (really streched)
planes2d          <- readARFF('regression_datasets/dataset_2201_2dplanes.arff') # Target: y
elevators         <- readARFF('regression_datasets/dataset_2202_elevators.arff') # Target: Goal
stock             <- readARFF('regression_datasets/dataset_2209_stock.arff') # Not regression task

regression_bench <- list()

regression_bench[[1]]  <- as.data.frame(wind)
regression_bench[[2]]  <- as.data.frame(communities_crime)
regression_bench[[3]]  <- as.data.frame(bank32nh)
regression_bench[[4]]  <- as.data.frame(wine_quality)
regression_bench[[5]]  <- as.data.frame(Mercedes_Benz)
regression_bench[[6]]  <- as.data.frame(kin8nm)
regression_bench[[7]]  <- as.data.frame(pol)
regression_bench[[8]]  <- as.data.frame(planes2d)
regression_bench[[9]]  <- as.data.frame(elevators)
regression_bench[[10]] <- as.data.frame(stock)

names(regression_bench) <- c('wind', 'us_crime', 'bank32nh', 'wine_quality', 
                             'Mercedes_Benz_Greener_Manufacturing', 'kin8nm', 'pol', 
                             '2dplanes', 'elevators', 'stock')

regression_bench <- regression_bench[3:9]
```

```{r eval=FALSE}
saveRDS(regression_bench, 'regression_bench.RData')
```

### Data Check

```{r}
regression_bench <- readRDS("regression_bench.RData")
```

#### bank32nh

```{r}
s <- check_data(regression_bench$bank32nh, 'rej')
```

#### wine_quality

```{r}
s <- check_data(regression_bench$wine_quality, 'quality')
```

#### Mercedes_Benz_Greener_Manufacturing

```{r}
s <- check_data(regression_bench$Mercedes_Benz_Greener_Manufacturing, 'y')
```

#### kin8nm

```{r}
s <- check_data(regression_bench$kin8nm, 'y')
```

#### pol

```{r}
s <- check_data(regression_bench$pol, 'foo')
```

#### 2dplanes

```{r}
s <- check_data(regression_bench$'2dplanes', 'y')
```

#### elevators

```{r}
s <- check_data(regression_bench$elevators, 'Goal')
```

## Summary

The results of this summary were created manually mostly based on this script. As seen below they are saved in the file named `data_issues_summary.csv` .

```{r}
data_summary <- read.csv('data_issues_summary.csv', sep = ';')
rmarkdown::paged_table(data_summary)
```
=======
---
title: "Ablation study of forester: Datasets Information"
author: "Hubert Ruczyński"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    theme: lumen
    toc_depth: 3
    number_sections: yes
    latex_engine: xelatex
---

```{css, echo=FALSE}
body .main-container {
  max-width: 1820px !important;
  width: 1820px !important;
}
body {
  max-width: 1820px !important;
  width: 1820px !important;
  font-family: Helvetica !important;
  font-size: 16pt !important;
}
h1,h2,h3,h4,h5,h6{
  font-size: 24pt !important;
}
```

# Downloads

The necessary downloads required for the forester package to work properly, if downloaded, the user can skip this part.

```{r eval = FALSE}
install.packages("devtools")
devtools::install_github("ModelOriented/forester")
devtools::install_github('catboost/catboost', subdir = 'catboost/R-package')
devtools::install_github('ricardo-bion/ggradar', dependencies = TRUE)
install.packages('tinytex')
tinytex::install_tinytex()
```

# Imports

Importing the necessary libraries.

```{r warning=FALSE, message=FALSE}
library(forester)
library(farff)
```

# Datasets analysis

In this section we will describe the datasets with the usage of `data_check()` function from the forester package.

## Binary classification

```{r}
binary_CC18 <- readRDS("binary_CC18.RData")
binary_CC18 <- binary_CC18[c(1, 2, 3, 4, 5, 19, 25, 26)]
```

### Data Check

#### kr-vs-kp

```{r}
s <- check_data(binary_CC18$`kr-vs-kp`, 'class')
```

#### breast-w

```{r}
s <- check_data(binary_CC18$`breast-w`, 'Class')
```

#### credit-approval

```{r}
s <- check_data(binary_CC18$`credit-approval`, 'class')
```

#### credit-g

```{r}
s <- check_data(binary_CC18$`credit-g`, 'class')
```

#### diabetes

```{r}
s <- check_data(binary_CC18$diabetes, 'class')
```

#### phoneme

```{r}
s <- check_data(binary_CC18$phoneme, 'Class')
```

#### banknote-authentication

```{r}
s <- check_data(binary_CC18$`banknote-authentication`, 'Class')
```

#### blood-transfusion-service-center

```{r}
s <- check_data(binary_CC18$`blood-transfusion-service-center`, 'Class')
```

## Regression

Loading widely used datasets from OpenML. If you are reproducing the paper step by step, skip this one, as we will load a specially prepared version in another cell.

```{r warning=FALSE, message=FALSE, eval=FALSE}
wind              <- readARFF('regression_datasets/wind.arff') # Not regression task
communities_crime <- readARFF('regression_datasets/phpeZQVCe.arff') # ViolentCrimesPerPop
bank32nh          <- readARFF('regression_datasets/phpYYZ4Qc.arff') # Target: rej
wine_quality      <- readARFF('regression_datasets/wine_quality.arff') # Target: quality
Mercedes_Benz     <- readARFF('regression_datasets/dataset.arff') # Target: y (2nd col)
Mercedes_Benz_y   <- Mercedes_Benz$y
Mercedes_Benz     <- Mercedes_Benz[, -2]
Mercedes_Benz$y   <- Mercedes_Benz_y # the last one
kin8nm            <- readARFF('regression_datasets/dataset_2175_kin8nm.arff') # Target: y
pol               <- readARFF('regression_datasets/dataset_2187_pol.arff') # Target: foo (really streched)
planes2d          <- readARFF('regression_datasets/dataset_2201_2dplanes.arff') # Target: y
elevators         <- readARFF('regression_datasets/dataset_2202_elevators.arff') # Target: Goal
stock             <- readARFF('regression_datasets/dataset_2209_stock.arff') # Not regression task

regression_bench <- list()

regression_bench[[1]]  <- as.data.frame(wind)
regression_bench[[2]]  <- as.data.frame(communities_crime)
regression_bench[[3]]  <- as.data.frame(bank32nh)
regression_bench[[4]]  <- as.data.frame(wine_quality)
regression_bench[[5]]  <- as.data.frame(Mercedes_Benz)
regression_bench[[6]]  <- as.data.frame(kin8nm)
regression_bench[[7]]  <- as.data.frame(pol)
regression_bench[[8]]  <- as.data.frame(planes2d)
regression_bench[[9]]  <- as.data.frame(elevators)
regression_bench[[10]] <- as.data.frame(stock)

names(regression_bench) <- c('wind', 'us_crime', 'bank32nh', 'wine_quality', 
                             'Mercedes_Benz_Greener_Manufacturing', 'kin8nm', 'pol', 
                             '2dplanes', 'elevators', 'stock')

regression_bench <- regression_bench[3:9]
```

```{r eval=FALSE}
saveRDS(regression_bench, 'regression_bench.RData')
```

### Data Check

```{r}
regression_bench <- readRDS("regression_bench.RData")
```

#### bank32nh

```{r}
s <- check_data(regression_bench$bank32nh, 'rej')
```

#### wine_quality

```{r}
s <- check_data(regression_bench$wine_quality, 'quality')
```

#### Mercedes_Benz_Greener_Manufacturing

```{r}
s <- check_data(regression_bench$Mercedes_Benz_Greener_Manufacturing, 'y')
```

#### kin8nm

```{r}
s <- check_data(regression_bench$kin8nm, 'y')
```

#### pol

```{r}
s <- check_data(regression_bench$pol, 'foo')
```

#### 2dplanes

```{r}
s <- check_data(regression_bench$'2dplanes', 'y')
```

#### elevators

```{r}
s <- check_data(regression_bench$elevators, 'Goal')
```

## Summary

The results of this summary were created manually mostly based on this script. As seen below they are saved in the file named `data_issues_summary.csv` .

```{r}
data_summary <- read.csv('data_issues_summary.csv', sep = ';')
rmarkdown::paged_table(data_summary)
```
>>>>>>> b6c9e7735ce229d9a94dce9db6fcedec62936c73
