---
title: "Ablation study of forester: Paper plots"
author: "Hubert Ruczyński"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    theme: lumen
    toc_depth: 3
    number_sections: yes
    latex_engine: xelatex
---

```{css, echo=FALSE}
body .main-container {
  max-width: 1820px !important;
  width: 1820px !important;
}
body {
  max-width: 1820px !important;
  width: 1820px !important;
  font-family: Helvetica !important;
  font-size: 16pt !important;
}
h1,h2,h3,h4,h5,h6{
  font-size: 24pt !important;
}
```

This is the notebook where the visualizations from `ablation_study_results_analysis` were enhanced and modified for the needs of paper.

# Imports and settings

```{r, warning=FALSE}
library(ggplot2)
library(patchwork)
library(scales)
```

# Data import

```{r}
duration_train_df               <- readRDS('ablation_processed_results/training_duration.RData')
duration_preprocessing          <- readRDS('ablation_processed_results/preprocessing_duration.RData')
extended_training_summary_table <- readRDS('ablation_processed_results/extended_training_summary_table.RData')
```

# Time analysis

```{r}
duration_df                                 <- duration_train_df
full_duration                               <- duration_preprocessing$Duration + duration_df$Duration
duration_df$Preprocessing_duration          <- duration_preprocessing$Duration
duration_df$Preprocessing_duration_fraction <- round(duration_df$Preprocessing_duration / full_duration, 3)
duration_df$Full_duration                   <- full_duration
rmarkdown::paged_table(duration_df)
```

## General time complexity

```{r, echo=FALSE}
column_fractions <- c()
max_fields_num   <- c()
task_type        <- c()
datasets         <- unique(extended_training_summary_table$Dataset)
for (i in 1:length(unique(extended_training_summary_table$Dataset))) {
  cols <- extended_training_summary_table[extended_training_summary_table$Dataset == datasets[i], 'Columns']
  rows <- extended_training_summary_table[extended_training_summary_table$Dataset == datasets[i], 'Rows']
  column_fractions <- c(column_fractions, round(min(cols) / max(cols), 2))
  max_fields_num   <- c(max_fields_num, max(rows) * max(cols))
  if (i > 8) {
      task_type <- c(task_type, 'regression')
    } else {
      task_type <- c(task_type, 'binary_classification')
    }
}
left_columns <- data.frame(Dataset = datasets, Column_fraction = column_fractions, 
                           Max_fields_number = max_fields_num, Task_type = task_type)
```

```{r fig.height=6, fig.width=20, echo=FALSE}
a <- ggplot(data = left_columns, aes(x = Column_fraction * 100, y = Dataset, color = Task_type, fill = Task_type)) + 
  geom_col(alpha = 0.5) + 
  theme_minimal() + 
  labs(title = 'Columns left (%)',
       subtitle = 'after maximal reduction',
       x = 'Columns [%]',
       y = '',
       color = 'Task_type',
       fill  = 'Task_type') +
  scale_color_manual(values = c("#afc968", "#74533d", "#7C843C")) +
  scale_fill_manual(values = c("#afc968", "#74533d", "#7C843C")) +
  theme(plot.title = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x = element_text(colour = 'black', size = 12),
        axis.title.y = element_text(colour = 'black', size = 12),
        axis.text.y = element_blank(),
        axis.text.x = element_text(colour = "black", size = 9)) + 
  theme(strip.background = element_rect(fill = "white", color = "white"),
        strip.text = element_text(size = 6 ), 
        legend.position = "none",
        strip.text.y.right = element_text(angle = 0))

b <- ggplot(data = duration_df, aes(x = Duration, y = Dataset, color = Task_type, fill = Task_type)) + 
  geom_boxplot(alpha = 0.5) + 
  theme_minimal() + 
  labs(title = 'Training time [s]',
       subtitle = '',
       x = 'Duration [s]',
       y = 'Dataset',
       color = 'Task_type',
       fill  = 'Task_type') +
  scale_color_manual(values = c("#afc968", "#74533d", "#7C843C")) +
  scale_fill_manual(values = c("#afc968", "#74533d", "#7C843C")) +
  scale_x_continuous(trans = log2_trans(), breaks = trans_breaks('log2', function(x) 2^x)) +
  annotation_logticks(base = 2, scaled = TRUE) +
  theme(plot.title = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x = element_text(colour = 'black', size = 12),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_text(colour = "black", size = 9)) + 
  theme(strip.background = element_rect(fill = "white", color = "white"),
        strip.text = element_text(size = 6 ), 
        legend.position = "bottom",
        strip.text.y.right = element_text(angle = 0))

c <- ggplot(data = left_columns, aes(x = Max_fields_number, y = Dataset, color = Task_type, fill = Task_type)) + 
  geom_col(alpha = 0.5) + 
  theme_minimal() + 
  labs(title = 'Initial fields',
       subtitle = '(no. rows times no. columns)',
       x = 'Number of fields',
       y = '',
       color = 'Task_type',
       fill  = 'Task_type') +
  scale_color_manual(values = c("#afc968", "#74533d", "#7C843C")) +
  scale_fill_manual(values  = c("#afc968", "#74533d", "#7C843C")) +
  scale_x_continuous(trans = log2_trans(), 
                     breaks = trans_breaks('log2', function(x) 2^x),
                     labels = trans_format('log2', math_format(2^.x))) +
  annotation_logticks(base = 2, scaled = TRUE) +
  theme(plot.title = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x = element_text(colour = 'black', size = 12),
        axis.title.y = element_text(colour = 'black', size = 12),
        axis.text.y = element_blank(),
        axis.text.x = element_text(colour = "black", size = 9)) + 
  theme(strip.background = element_rect(fill = "white", color = "white"),
        strip.text = element_text(size = 6 ), 
        legend.position = "none",
        strip.text.y.right = element_text(angle = 0))

d <- ggplot(data = duration_df, aes(x = Preprocessing_duration, y = Dataset, color = Task_type, fill = Task_type)) + 
  geom_boxplot(alpha = 0.5) + 
  theme_minimal() + 
  labs(title = 'Preprocessing time [s]',
       subtitle = '',
       x = 'Duration [s]',
       y = 'Dataset',
       color = 'Task_type',
       fill  = 'Task_type') +
  scale_color_manual(values = c("#afc968", "#74533d", "#7C843C")) +
  scale_fill_manual(values  = c("#afc968", "#74533d", "#7C843C")) +
  scale_x_continuous(trans = log2_trans(), breaks = trans_breaks('log2', function(x) 2^x)) +
  annotation_logticks(base = 2, scaled = TRUE) +
  theme(plot.title = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x = element_text(colour = 'black', size = 12),
        axis.title.y = element_text(colour = 'black', size = 12),
        axis.text.y = element_text(colour = "black", size = 9),
        axis.text.x = element_text(colour = "black", size = 9)) + 
  theme(strip.background = element_rect(fill = "white", color = "white"),
        strip.text = element_text(size = 6 ), 
        legend.position = "none",
        strip.text.y.right = element_text(angle = 0)) 

(d | b | c | a) + plot_layout(widths = c(3, 3, 1, 1))
```


```{r fig.height=6, fig.width=20, echo=FALSE}
e <- ggplot(data = duration_df, aes(x = Full_duration, y = Dataset, color = Task_type, fill = Task_type)) + 
  geom_boxplot(alpha = 0.5) + 
  theme_minimal() + 
  labs(title = 'Combined time',
       subtitle = 'of preprocessing and model training',
       x = 'Duration [s]',
       y = 'Dataset',
       color = 'Task_type',
       fill  = 'Task_type') +
  scale_color_manual(values = c("#afc968", "#74533d", "#7C843C")) +
  scale_fill_manual(values  = c("#afc968", "#74533d", "#7C843C")) +
  scale_x_continuous(trans = log2_trans(), breaks = trans_breaks('log2', function(x) 2^x)) +
  annotation_logticks(base = 2, scaled = TRUE) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x  = element_text(colour = 'black', size = 12),
        axis.title.y  = element_text(colour = 'black', size = 12),
        axis.text.y   = element_text(colour = "black", size = 9),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background = element_rect(fill = "white", color = "white"),
        strip.text = element_text(size = 6 ), 
        legend.position = "none",
        strip.text.y.right = element_text(angle = 0)) 

f <- ggplot(data = duration_df, aes(x = Preprocessing_duration_fraction * 100, y = Dataset, color = Task_type, fill = Task_type)) + 
  geom_boxplot(alpha = 0.5) + 
  theme_minimal() + 
  labs(title = 'Preprocessing time fraction',
       subtitle = 'as a part of full process length (%)',
       x = 'Preprocessing time [%]',
       y = 'Dataset',
       color = 'Task_type',
       fill  = 'Task_type') +
  scale_color_manual(values = c("#afc968", "#74533d", "#7C843C")) +
  scale_fill_manual(values  = c("#afc968", "#74533d", "#7C843C")) +
  xlim(0, 100) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x  = element_text(colour = 'black', size = 12),
        axis.title.y  = element_blank(),
        axis.text.y   = element_blank(),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background = element_rect(fill = "white", color = "white"),
        strip.text = element_text(size = 6 ), 
        legend.position = "bottom",
        strip.text.y.right = element_text(angle = 0))

(e | f | c | a) + plot_layout(widths = c(3, 3, 1, 1))
```

## Preprocessing time complexity


```{r fig.height=6, fig.width=15, echo=FALSE}
bool_fs <- duration_preprocessing
bool_fs[bool_fs$Feature_selection != 'none', 'Feature_selection'] <- 'yes'

g <- ggplot(data = bool_fs, aes(x = Duration, y = Dataset, color = factor(Feature_selection), fill = factor(Feature_selection))) + 
  geom_boxplot(alpha = 0.5) + 
  theme_minimal() + 
  labs(title = 'Preprocessing time comparison',
       subtitle = 'if any feature selection method was used or not',
       x = 'Duration [s]',
       y = 'Dataset',
       color = 'Feature Selection',
       fill  = 'Feature Selection') +
  scale_color_manual(values = c("#afc968", "#74533d", "#7C843C")) +
  scale_fill_manual(values = c("#afc968", "#74533d", "#7C843C")) +
  scale_x_continuous(trans = log2_trans(), breaks = trans_breaks('log2', function(x) 2^x)) +
  annotation_logticks(base = 2, scaled = TRUE) +
  theme(plot.title = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x = element_text(colour = 'black', size = 12),
        axis.title.y = element_text(colour = 'black', size = 12),
        axis.text.y = element_text(colour = "black", size = 9),
        axis.text.x = element_text(colour = "black", size = 9)) + 
  theme(strip.background = element_rect(fill = "white", color = "white"),
        strip.text = element_text(size = 6 ), 
        legend.position = "bottom",
        strip.text.y.right = element_text(angle = 0))

g
```

```{r fig.height=6, fig.width=15, echo=FALSE}
no_fs <- duration_preprocessing[duration_preprocessing$Feature_selection == 'none', ]

h <- ggplot(data = no_fs, aes(x = Duration, y = Dataset, color = factor(Removal), fill = factor(Removal))) + 
  geom_boxplot(alpha = 0.5) + 
  theme_minimal() + 
  labs(title = 'Preprocessing time comparison',
       subtitle = 'depending on removal strategy when no feature selection method is used',
       x = 'Duration [s]',
       y = 'Dataset',
       color = 'Removal strategy',
       fill  = 'Removal strategy') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C")) +
  scale_x_continuous(trans = log2_trans(), breaks = trans_breaks('log2', function(x) 2^x)) +
  annotation_logticks(base = 2, scaled = TRUE) +
  theme(plot.title = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x = element_text(colour = 'black', size = 12),
        axis.title.y = element_text(colour = 'black', size = 12),
        axis.text.y = element_text(colour = "black", size = 9),
        axis.text.x = element_text(colour = "black", size = 9)) + 
  theme(strip.background = element_rect(fill = "white", color = "white"),
        strip.text = element_text(size = 6 ), 
        legend.position = "bottom",
        strip.text.y.right = element_text(angle = 0))

h
```

### Appendix Imputation

```{r fig.height=4, fig.width=10, echo=FALSE}
no_fs_imp <- no_fs[no_fs$Dataset %in% c('breast-w', 'credit-approval'), ]
i <- ggplot(data = no_fs_imp, aes(x = Duration, y = Dataset, color = factor(Imputation), fill = factor(Imputation))) + 
  geom_boxplot(alpha = 0.5) + 
  theme_minimal() + 
  labs(title = 'Preprocessing time comparison with forester',
       subtitle = 'for different ML tasks, divided by removal strategy',
       x = 'Duration [s]',
       y = 'Dataset',
       color = 'Imputation strategy',
       fill  = 'Imputation strategy') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  scale_x_continuous(trans = log2_trans(), breaks = trans_breaks('log2', function(x) 2^x)) +
  annotation_logticks(base = 2, scaled = TRUE) +
  theme(plot.title = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x = element_text(colour = 'black', size = 12),
        axis.title.y = element_text(colour = 'black', size = 12),
        axis.text.y = element_text(colour = "black", size = 9),
        axis.text.x = element_text(colour = "black", size = 9)) + 
  theme(strip.background = element_rect(fill = "white", color = "white"),
        strip.text = element_text(size = 6 ), 
        legend.position = "bottom",
        strip.text.y.right = element_text(angle = 0))
i
```

```{r fig.height=8, fig.width=15, echo=FALSE}
j <- ggplot(data = no_fs, aes(x = Duration, y = Dataset, color = factor(Imputation), fill = factor(Imputation))) + 
  geom_boxplot(alpha = 0.5) + 
  theme_minimal() + 
  labs(title = 'Preprocessing time comparison with forester',
       subtitle = 'for different ML tasks, divided by imputation strategy',
       x = 'Duration [s]',
       y = 'Dataset',
       color = 'Imputation strategy',
       fill  = 'Imputation strategy') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  scale_x_continuous(trans = log2_trans(), breaks = trans_breaks('log2', function(x) 2^x)) +
  annotation_logticks(base = 2, scaled = TRUE) +
  theme(plot.title = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x = element_text(colour = 'black', size = 12),
        axis.title.y = element_text(colour = 'black', size = 12),
        axis.text.y = element_text(colour = "black", size = 9),
        axis.text.x = element_text(colour = "black", size = 9)) + 
  theme(strip.background = element_rect(fill = "white", color = "white"),
        strip.text = element_text(size = 6 ), 
        legend.position = "bottom",
        strip.text.y.right = element_text(angle = 0))

j
```

## Feature selection time complexity

```{r fig.height=8, fig.width=15, echo=FALSE}
only_fs       <- duration_preprocessing[duration_preprocessing$Feature_selection != 'none', ]
only_fs_niche <- only_fs[only_fs$Feature_selection %in% c('MI', 'MCFS'), ]
only_fs_top   <- only_fs[only_fs$Feature_selection %in% c('VI', 'BORUTA'), ]

datasets <- unique(only_fs$Dataset)
VI       <- c()
MCFS     <- c()
MI       <- c()
BORUTA   <- c()

for (i in unique(only_fs$Dataset)) {
  ds     <- only_fs[only_fs$Dataset == i, ]
  VI     <- c(VI,     median(ds[ds$Feature_selection == 'VI', 'Duration']))
  MCFS   <- c(MCFS,   median(ds[ds$Feature_selection == 'MCFS', 'Duration']))
  MI     <- c(MI,     median(ds[ds$Feature_selection == 'MI', 'Duration']))
  BORUTA <- c(BORUTA, median(ds[ds$Feature_selection == 'BORUTA', 'Duration']))
}

median_fs      <- data.frame(Dataset = datasets, VI = VI, MCFS = MCFS, BORUTA = BORUTA, MI = MI)
long_median_fs <- reshape(median_fs, varying = c('MI' ,'VI', 'MCFS', 'BORUTA'), v.names = c('Duration'), 
                          times = c('MI' ,'VI', 'MCFS', 'BORUTA'), direction = 'long')
long_median_fs <- long_median_fs[, 1:3]

rownames(long_median_fs) <- NULL
colnames(long_median_fs) <- c('Dataset', 'Method', 'Duration')

k <- ggplot(data = only_fs, aes(x = Duration, y = Dataset, color = factor(Feature_selection), fill = factor(Feature_selection))) + 
  geom_boxplot(alpha = 0.5) + 
  theme_minimal() + 
  labs(title = 'Preprocessing time comparison',
       subtitle = 'depending on feature selection method',
       x = 'Duration [s]',
       y = 'Dataset',
       color = 'Feature Selection',
       fill  = 'Feature Selection') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_x_continuous(trans = log2_trans(), breaks = trans_breaks('log2', function(x) 2^x), limits = c(NA, 4100)) +
  annotation_logticks(base = 2, scaled = TRUE) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x  = element_text(colour = 'black', size = 12),
        axis.title.y  = element_text(colour = 'black', size = 12),
        axis.text.y   = element_text(colour = "black", size = 9),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background = element_rect(fill = "white", color = "white"),
        strip.text = element_text(size = 6 ), 
        legend.position = "bottom",
        strip.text.y.right = element_text(angle = 0))

l <- ggplot(data = long_median_fs, aes(x = Duration, y = Dataset, color = factor(Method), fill = factor(Method))) + 
  geom_point(size = 5, alpha = 0.5) + 
  theme_minimal() + 
  labs(title = 'Preprocessing time comparison',
       subtitle = 'aggregated with median value',
       x = 'Duration [s]',
       y = 'Dataset',
       color = 'Feature Selection',
       fill  = 'Feature Selection') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_x_continuous(trans = log2_trans(), breaks = trans_breaks('log2', function(x) 2^x), limits = c(NA, 4100)) +
  annotation_logticks(base = 2, scaled = TRUE) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x  = element_text(colour = 'black', size = 12),
        axis.title.y  = element_blank(),
        axis.text.y   = element_blank(),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background = element_rect(fill = "white", color = "white"),
        strip.text = element_text(size = 6 ), 
        legend.position = "none",
        strip.text.y.right = element_text(angle = 0))

k | l
```


```{r fig.height=6, fig.width=15, echo=FALSE}
long_median_fs_slow <- long_median_fs[long_median_fs$Method %in% c('VI', 'MCFS'), ]
long_median_fs_fast <- long_median_fs[long_median_fs$Method %in% c('BORUTA', 'MI'), ]

m <- ggplot(data = long_median_fs_slow, aes(x = Duration, y = Dataset, color = factor(Method), fill = factor(Method))) + 
  geom_point(size = 5, alpha = 0.5) + 
  theme_minimal() + 
  labs(title = 'Preprocessing median time comparison',
       subtitle = 'for slow feature selection methods',
       x = 'Duration [s]',
       y = 'Dataset',
       color = 'Feature Selection',
       fill  = 'Feature Selection') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_x_continuous(trans = log2_trans(), breaks = trans_breaks('log2', function(x) 2^x)) +
  annotation_logticks(base = 2, scaled = TRUE) +
  theme(plot.title = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x = element_text(colour = 'black', size = 12),
        axis.title.y = element_text(colour = 'black', size = 12),
        axis.text.y = element_text(colour = "black", size = 9),
        axis.text.x = element_text(colour = "black", size = 9)) + 
  theme(strip.background = element_rect(fill = "white", color = "white"),
        strip.text = element_text(size = 6 ), 
        legend.position = "bottom",
        strip.text.y.right = element_text(angle = 0))

n <- ggplot(data = long_median_fs_fast, aes(x = Duration, y = Dataset, color = factor(Method), fill = factor(Method))) + 
  geom_point(size = 5, alpha = 0.5) + 
  theme_minimal() + 
  labs(title = 'Preprocessing median time comparison',
       subtitle = 'for fast feature selection methods',
       x = 'Duration [s]',
       y = 'Dataset',
       color = 'Feature Selection',
       fill  = 'Feature Selection') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_x_continuous(trans = log2_trans(), breaks = trans_breaks('log2', function(x) 2^x)) +
  annotation_logticks(base = 2, scaled = TRUE) +
  theme(plot.title = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x = element_text(colour = 'black', size = 12),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_text(colour = "black", size = 9)) + 
  theme(strip.background = element_rect(fill = "white", color = "white"),
        strip.text = element_text(size = 6 ), 
        legend.position = "bottom",
        strip.text.y.right = element_text(angle = 0))
m | n
```

# Performance

```{r, echo=FALSE}
all_engines               <- extended_training_summary_table[extended_training_summary_table$Engine == 'all', ]
all_engines_bin           <- all_engines[all_engines$Task_type == 'binary_classification', ]
all_engines_reg           <- all_engines[all_engines$Task_type == 'regression', ]
all_engines_bin_baselines <- all_engines_bin[which(all_engines_bin$Removal =='removal_min' & 
                                                   all_engines_bin$Imputation =='median-other' & 
                                                   all_engines_bin$Feature_selection =='none'), ]
all_engines_bin_baselines <- all_engines_bin_baselines[c(1:3, 7:9, 13:15, 19:21, 25:27, 31:33, 37:39, 43:45), ]
all_engines_reg_baselines <- all_engines_reg[which(all_engines_reg$Removal =='removal_min' & 
                                                   all_engines_reg$Imputation =='median-other' & 
                                                   all_engines_reg$Feature_selection =='none'), ]
all_engines_reg_baselines <- all_engines_reg_baselines[c(1:4, 9:12, 17:20, 25:28, 33:36, 41:44, 49:52), ]
```

## Advanced preprocessing vs Baseline

```{r fig.height=8, fig.width=20, echo=FALSE}
o <- ggplot(data = all_engines_bin, aes(x = Max, y = Dataset, color = factor(Metric), fill = factor(Metric))) + 
  geom_boxplot(alpha = 0.5) +
  geom_point(data = all_engines_bin_baselines, size = 3, shape = 4, 
             position = position_jitterdodge(), 
             aes(x = Max, y = Dataset, color = factor(Metric), fill = factor(Metric))) +
  theme_minimal() + 
  labs(title = 'Max metrics values with different preprocessing strategies',
       subtitle = 'for different binary classification tasks, divided by metric',
       x = 'Value',
       y = 'Dataset',
       color = 'Metric',
       fill  = 'Metric') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x  = element_text(colour = 'black', size = 12),
        axis.title.y  = element_text(colour = 'black', size = 12),
        axis.text.y   = element_text(colour = "black", size = 9),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "none",
        strip.text.y.right = element_text(angle = 0))

p <- ggplot(data = all_engines_bin, aes(x = Mean, y = Dataset, color = factor(Metric), fill = factor(Metric))) + 
  geom_boxplot(alpha = 0.5) + 
  geom_point(data = all_engines_bin_baselines, size = 3, shape = 4, 
             position = position_jitterdodge(), 
             aes(x = Mean, y = Dataset, color = factor(Metric), fill = factor(Metric))) +
  theme_minimal() + 
  labs(title = 'Mean metrics values',
       subtitle = 'for different binary classification tasks, divided by metric',
       x = 'Value',
       y = 'Dataset',
       color = 'Metric',
       fill  = 'Metric') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_blank(),
        axis.title.x  = element_text(colour = 'black', size = 12),
        axis.title.y  = element_blank(),
        axis.text.y   = element_blank(),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "bottom",
        strip.text.y.right = element_text(angle = 0))

r <- ggplot(data = all_engines_bin, aes(x = Median, y = Dataset, color = factor(Metric), fill = factor(Metric))) + 
  geom_boxplot(alpha = 0.5) + 
  geom_point(data = all_engines_bin_baselines, size = 3, shape = 4, 
             position = position_jitterdodge(), 
             aes(x = Median, y = Dataset, color = factor(Metric), fill = factor(Metric))) +
  theme_minimal() + 
  labs(title = 'Median metrics values',
       subtitle = 'for different binary classification tasks, divided by metric',
       x = 'Value',
       y = 'Dataset',
       color = 'Metric',
       fill  = 'Metric') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_blank(),
        axis.title.x  = element_text(colour = 'black', size = 12),
        axis.title.y  = element_blank(),
        axis.text.y   = element_blank(),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "none",
        strip.text.y.right = element_text(angle = 0))

o | p | r
```

```{r echo=FALSE}
all_engines_reg_min_med <- all_engines_reg[, c(1, 2, 3, 4, 5, 13, 16, 17)]
median                  <- all_engines_reg_min_med[, 1:7]
names(median)           <- c(names(median)[1:6], 'Value')
min                     <- all_engines_reg_min_med[, c(1:6, 8)]
names(min)              <- c(names(min)[1:6], 'Value')
all_engines_reg_min_med <- rbind(median, min)
all_engines_reg_min_med$Aggregation <- rep(c('Median', 'Min'), each = nrow(all_engines_reg))
```

```{r echo=FALSE}
all_engines_reg_baselines_min_med <- all_engines_reg_baselines[, c(1, 2, 3, 4, 5, 13, 16, 17)]
median                            <- all_engines_reg_baselines_min_med[, 1:7]
names(median)                     <- c(names(median)[1:6], 'Value')
min                               <- all_engines_reg_baselines_min_med[, c(1:6, 8)]
names(min)                        <- c(names(min)[1:6], 'Value')
all_engines_reg_baselines_min_med <- rbind(median, min)
all_engines_reg_baselines_min_med$Aggregation <- rep(c('Median', 'Min'), each = nrow(all_engines_reg_baselines))
```

```{r fig.height=8, fig.width=15, echo=FALSE, warning=FALSE}
metric <- 'mse'
s <- ggplot(data = all_engines_reg_min_med[which(all_engines_reg_min_med$Metric == metric), ], 
            aes(x = Value, y = Dataset, color = factor(Aggregation), fill = factor(Aggregation))) + 
  geom_boxplot(alpha = 0.5) +
  geom_point(data = all_engines_reg_baselines_min_med[which(all_engines_reg_min_med$Metric == metric), ], 
             size = 3, shape = 4,position = position_jitterdodge(), 
             aes(x = Value, y = Dataset, color = factor(Aggregation), fill = factor(Aggregation))) +
  theme_minimal() + 
  labs(title    = 'Aggregated MSE (Magnified)',
       subtitle = 'for different regression tasks and preprocessing strategies',
       x        = 'Value',
       y        = 'Dataset',
       color    = 'Aggregation',
       fill     = 'Aggregation') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  coord_cartesian(xlim = c(0, 2)) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x  = element_blank(),
        axis.title.y  = element_blank(),
        axis.text.y   = element_text(colour = "black", size = 9),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "none",
        strip.text.y.right = element_text(angle = 0))

t <- ggplot(data = all_engines_reg_min_med[all_engines_reg_min_med$Metric == metric, ], 
            aes(x = Value, y = Dataset, color = factor(Aggregation), fill = factor(Aggregation))) + 
  geom_boxplot(alpha = 0.5) +
  geom_point(data = all_engines_reg_baselines_min_med[which(all_engines_reg_min_med$Metric == metric), ], 
             size = 3, shape = 4,position = position_jitterdodge(), 
             aes(x = Value, y = Dataset, color = factor(Aggregation), fill = factor(Aggregation))) +
  theme_minimal() + 
  labs(title    = 'Aggregated MSE',
       x        = 'Value',) +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  coord_cartesian(xlim = c(0, NA)) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_blank(),
        axis.title.x  = element_blank(),
        axis.title.y  = element_blank(),
        axis.text.y   = element_blank(),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "none",
        strip.text.y.right = element_text(angle = 0))

metric <- 'mae'
u <- ggplot(data = all_engines_reg_min_med[which(all_engines_reg_min_med$Metric == metric), ], 
            aes(x = Value, y = Dataset, color = factor(Aggregation), fill = factor(Aggregation))) + 
  geom_boxplot(alpha = 0.5) +
  geom_point(data = all_engines_reg_baselines_min_med[which(all_engines_reg_min_med$Metric == metric), ], 
             size = 3, shape = 4,position = position_jitterdodge(), 
             aes(x = Value, y = Dataset, color = factor(Aggregation), fill = factor(Aggregation))) +
  theme_minimal() + 
  labs(title    = 'Aggregated MAE (Magnified)',
       x        = 'Value',
       y        = 'Dataset',
       color    = 'Aggregation',
       fill     = 'Aggregation') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  coord_cartesian(xlim = c(0, 2)) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_blank(),
        axis.title.x  = element_blank(),
        axis.title.y  = element_text(colour = 'black', size = 12),
        axis.text.y   = element_text(colour = "black", size = 9),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "none",
        strip.text.y.right = element_text(angle = 0))

v <- ggplot(data = all_engines_reg_min_med[all_engines_reg_min_med$Metric == metric, ], 
            aes(x = Value, y = Dataset, color = factor(Aggregation), fill = factor(Aggregation))) + 
  geom_boxplot(alpha = 0.5) +
  geom_point(data = all_engines_reg_baselines_min_med[which(all_engines_reg_min_med$Metric == metric), ], 
             size = 3, shape = 4,position = position_jitterdodge(), 
             aes(x = Value, y = Dataset, color = factor(Aggregation), fill = factor(Aggregation))) +
  theme_minimal() + 
  labs(title    = 'Aggregated MAE',
       x        = 'Value',) +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  coord_cartesian(xlim = c(0, NA)) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_blank(),
        axis.title.x  = element_blank(),
        axis.title.y  = element_blank(),
        axis.text.y   = element_blank(),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "none",
        strip.text.y.right = element_text(angle = 0))

metric <- 'rmse'
w <- ggplot(data = all_engines_reg_min_med[which(all_engines_reg_min_med$Metric == metric), ], 
            aes(x = Value, y = Dataset, color = factor(Aggregation), fill = factor(Aggregation))) + 
  geom_boxplot(alpha = 0.5) +
  geom_point(data = all_engines_reg_baselines_min_med[which(all_engines_reg_min_med$Metric == metric), ], 
             size = 3, shape = 4,position = position_jitterdodge(), 
             aes(x = Value, y = Dataset, color = factor(Aggregation), fill = factor(Aggregation))) +
  theme_minimal() + 
  labs(title    = 'Aggregated RMSE (Magnified)',
       x        = 'Value',
       y        = 'Dataset',
       color    = 'Aggregation',
       fill     = 'Aggregation') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  coord_cartesian(xlim = c(0, 2)) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_blank(),
        axis.title.x  = element_text(colour = 'black', size = 12),
        axis.title.y  = element_blank(),
        axis.text.y   = element_text(colour = "black", size = 9),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "bottom",
        strip.text.y.right = element_text(angle = 0))

x <- ggplot(data = all_engines_reg_min_med[all_engines_reg_min_med$Metric == metric, ], 
            aes(x = Value, y = Dataset, color = factor(Aggregation), fill = factor(Aggregation))) + 
  geom_boxplot(alpha = 0.5) +
  geom_point(data = all_engines_reg_baselines_min_med[which(all_engines_reg_min_med$Metric == metric), ], 
             size = 3, shape = 4,position = position_jitterdodge(), 
             aes(x = Value, y = Dataset, color = factor(Aggregation), fill = factor(Aggregation))) +
  theme_minimal() + 
  labs(title    = 'Aggregated RMSE',
       x        = 'Value',) +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  coord_cartesian(xlim = c(0, NA)) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_blank(),
        axis.title.x  = element_text(colour = 'black', size = 12),
        axis.title.y  = element_blank(),
        axis.text.y   = element_blank(),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "none",
        strip.text.y.right = element_text(angle = 0))

(s | t) / (u | v) / (w | x)
```


## FS impact on performance

```{r echo=FALSE}
all_engines_bin_fs <- all_engines_bin
all_engines_bin_fs <- all_engines_bin_fs[all_engines_bin_fs$Metric == 'accuracy', ]
all_engines_bin_fs$Feature_selection <- ifelse(all_engines_bin_fs$Feature_selection != 'none', 'yes', 'none')
all_engines_reg_min_med_fs <- all_engines_reg_min_med
all_engines_reg_min_med_fs <- all_engines_reg_min_med_fs[all_engines_reg_min_med_fs$Metric == 'rmse', ]
all_engines_reg_min_med_fs$Feature_selection <- ifelse(all_engines_reg_min_med_fs$Feature_selection != 'none', 'yes', 'none')
```

```{r fig.height=6, fig.width=20, echo=FALSE, warning=FALSE}
a1 <- ggplot(data = all_engines_bin_fs, aes(x = Max, y = Dataset, color = factor(Feature_selection), fill = factor(Feature_selection))) + 
  geom_boxplot(alpha = 0.5) +
  geom_point(data = all_engines_bin_baselines[all_engines_bin_baselines$Metric == 'accuracy', ], 
             size = 5, shape = 4, aes(x = Max, y = Dataset), color = '#B1805B', fill = '#B1805B') +
  theme_minimal() + 
  labs(title = 'Max Accuracy values',
       subtitle = 'if FS methods were used for binary classification tasks',
       x = 'Value',
       y = 'Dataset',
       color = 'Metric',
       fill  = 'Metric') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  xlim(0.35, 1) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x  = element_blank(),
        axis.title.y  = element_blank(),
        axis.text.y   = element_text(colour = "black", size = 9),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "none",
        strip.text.y.right = element_text(angle = 0))

b1 <- ggplot(data = all_engines_bin_fs, aes(x = Mean, y = Dataset, color = factor(Feature_selection), fill = factor(Feature_selection))) + 
  geom_boxplot(alpha = 0.5) + 
  geom_point(data = all_engines_bin_baselines[all_engines_bin_baselines$Metric == 'accuracy', ], 
             size = 5, shape = 4, aes(x = Mean, y = Dataset), color = '#B1805B', fill = '#B1805B') +
  theme_minimal() + 
  labs(title = 'Mean Accuracy values',
       subtitle = '',
       x = 'Value',
       y = 'Dataset',
       color = 'Metric',
       fill  = 'Metric') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  xlim(0.35, 1) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_blank(),
        axis.title.x  = element_blank(),
        axis.title.y  = element_blank(),
        axis.text.y   = element_text(colour = "black", size = 9),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "none",
        strip.text.y.right = element_text(angle = 0))

d1 <- ggplot(data = all_engines_reg_min_med_fs[all_engines_reg_min_med_fs$Aggregation == 'Min', ],
            aes(x = Value, y = Dataset, color = factor(Feature_selection), fill = factor(Feature_selection))) + 
  geom_boxplot(alpha = 0.5) +
  geom_point(data = all_engines_reg_baselines_min_med[which(all_engines_reg_baselines_min_med$Metric == 'rmse' & 
                                                            all_engines_reg_baselines_min_med$Aggregation == 'Min'), ], 
             size = 4, shape = 4, aes(x = Value, y = Dataset), color = '#B1805B', fill = '#B1805B') +
  theme_minimal() + 
  labs(title    = 'Minimal RMSE values (Magnified)',
       subtitle = 'if FS methods were used for regression tasks',
       x        = 'RMSE',
       y        = 'Dataset',
       color    = 'Feature_selection',
       fill     = 'Feature_selection') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  coord_cartesian(xlim = c(0, 1.5)) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x  = element_blank(),
        axis.title.y  = element_blank(),
        axis.text.y   = element_blank(),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "none",
        strip.text.y.right = element_text(angle = 0))

e1 <- ggplot(data = all_engines_reg_min_med_fs[all_engines_reg_min_med_fs$Aggregation == 'Min', ],  
            aes(x = Value, y = Dataset, color = factor(Feature_selection), fill = factor(Feature_selection))) + 
  geom_boxplot(alpha = 0.5) +
  geom_point(data = all_engines_reg_baselines_min_med[which(all_engines_reg_baselines_min_med$Metric == 'rmse' & 
                                                            all_engines_reg_baselines_min_med$Aggregation == 'Min'), ], 
             size = 4, shape = 4, aes(x = Value, y = Dataset), color = '#B1805B', fill = '#B1805B') +
  theme_minimal() + 
  labs(title    = 'Minimal RMSE values',
       x        = 'RMSE',) +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  coord_cartesian(xlim = c(0, NA)) +
  scale_y_discrete(position = "right") +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_blank(),
        axis.title.x  = element_blank(),
        axis.title.y  = element_blank(),
        axis.text.y   = element_text(colour = "black", size = 9),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "none",
        strip.text.y.right = element_text(angle = 0))

f1 <- ggplot(data = all_engines_reg_min_med_fs[all_engines_reg_min_med_fs$Aggregation == 'Median', ],
            aes(x = Value, y = Dataset, color = factor(Feature_selection), fill = factor(Feature_selection))) + 
  geom_boxplot(alpha = 0.5) +
  geom_point(data = all_engines_reg_baselines_min_med[which(all_engines_reg_baselines_min_med$Metric == 'rmse' & 
                                                            all_engines_reg_baselines_min_med$Aggregation == 'Median'), ], 
             size = 4, shape = 4, aes(x = Value, y = Dataset), color = '#B1805B', fill = '#B1805B') +
  theme_minimal() + 
  labs(title    = 'Median RMSE values (Magnified)',
       x        = 'RMSE',
       y        = 'Dataset',
       color    = 'Feature_selection',
       fill     = 'Feature_selection') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  coord_cartesian(xlim = c(0, 1.5)) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_blank(),
        axis.title.x  = element_blank(),
        axis.title.y  = element_blank(),
        axis.text.y   = element_blank(),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "bottom",
        strip.text.y.right = element_text(angle = 0))

g1 <- ggplot(data = all_engines_reg_min_med_fs[all_engines_reg_min_med_fs$Aggregation == 'Median', ], 
            aes(x = Value, y = Dataset, color = factor(Feature_selection), fill = factor(Feature_selection))) + 
  geom_boxplot(alpha = 0.5) +
  geom_point(data = all_engines_reg_baselines_min_med[which(all_engines_reg_baselines_min_med$Metric == 'rmse' & 
                                                            all_engines_reg_baselines_min_med$Aggregation == 'Median'), ], 
             size = 4, shape = 4, aes(x = Value, y = Dataset), color = '#B1805B', fill = '#B1805B') +
  theme_minimal() + 
  labs(title    = 'Median RMSE values',
       x        = 'RMSE',) +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  coord_cartesian(xlim = c(0, NA)) +
  scale_y_discrete(position = "right") +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_blank(),
        axis.title.x  = element_blank(),
        axis.title.y  = element_blank(),
        axis.text.y   = element_text(colour = "black", size = 9),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "none",
        strip.text.y.right = element_text(angle = 0))

((a1 / b1) | (plot_spacer() / plot_spacer()) | (d1 / f1) | (e1 / g1)) + plot_layout(widths = c(5, 0.5, 4, 4))

```

## Removal impact on performance

### Binary Classification

```{r echo=FALSE}
all_engines_bin_no_fs <- all_engines_bin_fs[all_engines_bin_fs$Feature_selection == 'none', ]
all_engines_reg_no_fs <- all_engines_reg_min_med_fs[all_engines_reg_min_med_fs$Feature_selection == 'none', ]
```

```{r fig.height=6, fig.width=20, echo=FALSE, warning=FALSE}
h1 <- ggplot(data = all_engines_bin_no_fs, aes(x = Max, y = Dataset, color = factor(Removal), fill = factor(Removal))) + 
  geom_boxplot(alpha = 0.5) +
  geom_point(data = all_engines_bin_baselines[all_engines_bin_baselines$Metric == 'accuracy', ], 
             size = 5, shape = 4, aes(x = Max, y = Dataset), color = '#B1805B', fill = '#B1805B') +
  theme_minimal() + 
  labs(title = 'Max Accuracy',
       subtitle = 'without FS used for different binary classification tasks',
       x = 'Value',
       y = 'Dataset',
       color = 'Removal strategy',
       fill  = 'Removal strategy') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  xlim(0.93, 1) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x  = element_blank(),
        axis.title.y  = element_blank(),
        axis.text.y   = element_text(colour = "black", size = 9),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "none",
        strip.text.y.right = element_text(angle = 0))

i1 <- ggplot(data = all_engines_bin_no_fs, aes(x = Mean, y = Dataset, color = factor(Removal), fill = factor(Removal))) + 
  geom_boxplot(alpha = 0.5) +
  geom_point(data = all_engines_bin_baselines[all_engines_bin_baselines$Metric == 'accuracy', ], 
             size = 5, shape = 4, aes(x = Mean, y = Dataset), color = '#B1805B', fill = '#B1805B') +
  theme_minimal() + 
  labs(title = 'Mean Accuracy',
       subtitle = 'for different binary classification tasks',
       x = 'Value',
       y = 'Dataset',
       color = 'Removal strategy',
       fill  = 'Removal strategy') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  xlim(0.8, 1) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_blank(),
        axis.title.x  = element_blank(),
        axis.title.y  = element_blank(),
        axis.text.y   = element_text(colour = "black", size = 9),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "none",
        strip.text.y.right = element_text(angle = 0))

l1 <- ggplot(data = all_engines_reg_no_fs[all_engines_reg_no_fs$Aggregation == 'Median', ], 
             aes(x = Value, y = Dataset, color = factor(Removal), fill = factor(Removal))) + 
  geom_boxplot(alpha = 0.5) +
  geom_point(data = all_engines_reg_baselines_min_med[which(all_engines_reg_baselines_min_med$Metric == 'rmse' & 
                                                            all_engines_reg_baselines_min_med$Aggregation == 'Median'), ], 
             size = 4, shape = 4, aes(x = Value, y = Dataset), color = '#B1805B', fill = '#B1805B') +
  theme_minimal() + 
  labs(title = 'Median RMSE (Magnified)',
       subtitle = 'without FS used for different regression tasks',
       x = 'RMSE',
       y = 'Dataset',
       color = 'Removal strategy',
       fill  = 'Removal strategy') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  xlim(0, 1.3) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x  = element_blank(),
        axis.title.y  = element_blank(),
        axis.text.y   = element_blank(),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "none",
        strip.text.y.right = element_text(angle = 0))

m1 <- ggplot(data = all_engines_reg_no_fs[all_engines_reg_no_fs$Aggregation == 'Median', ], 
             aes(x = Value, y = Dataset, color = factor(Removal), fill = factor(Removal))) + 
  geom_boxplot(alpha = 0.5) +
  geom_point(data = all_engines_reg_baselines_min_med[which(all_engines_reg_baselines_min_med$Metric == 'rmse' & 
                                                            all_engines_reg_baselines_min_med$Aggregation == 'Median'), ], 
             size = 4, shape = 4, aes(x = Value, y = Dataset), color = '#B1805B', fill = '#B1805B') +
  theme_minimal() + 
  labs(title = 'Median RMSE',
       subtitle = 'without FS used for different regression tasks',
       x = 'RMSE',
       y = 'Dataset',
       color = 'Removal strategy',
       fill  = 'Removal strategy') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  xlim(8.5, NA) +
  scale_y_discrete(position = "right") +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x  = element_blank(),
        axis.title.y  = element_blank(),
        axis.text.y   = element_text(colour = "black", size = 9),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "none",
        strip.text.y.right = element_text(angle = 0))

n1 <- ggplot(data = all_engines_reg_no_fs[all_engines_reg_no_fs$Aggregation == 'Min', ], 
             aes(x = Value, y = Dataset, color = factor(Removal), fill = factor(Removal))) + 
  geom_boxplot(alpha = 0.5) +
  geom_point(data = all_engines_reg_baselines_min_med[which(all_engines_reg_baselines_min_med$Metric == 'rmse' & 
                                                            all_engines_reg_baselines_min_med$Aggregation == 'Min'), ], 
             size = 4, shape = 4, aes(x = Value, y = Dataset), color = '#B1805B', fill = '#B1805B') +
  theme_minimal() + 
  labs(title = 'Minimal (Magnified)',
       subtitle = 'for different regression tasks',
       x = 'RMSE',
       y = 'Dataset',
       color = 'Removal strategy',
       fill  = 'Removal strategy') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  xlim(0, 0.25) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_blank(),
        axis.title.x  = element_text(colour = 'black', size = 12),
        axis.title.y  = element_blank(),
        axis.text.y   = element_blank(),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "bottom",
        strip.text.y.right = element_text(angle = 0))

o1 <- ggplot(data = all_engines_reg_no_fs[all_engines_reg_no_fs$Aggregation == 'Min', ], 
             aes(x = Value, y = Dataset, color = factor(Removal), fill = factor(Removal))) + 
  geom_boxplot(alpha = 0.5) +
  geom_point(data = all_engines_reg_baselines_min_med[which(all_engines_reg_baselines_min_med$Metric == 'rmse' & 
                                                            all_engines_reg_baselines_min_med$Aggregation == 'Min'), ], 
             size = 4, shape = 4, aes(x = Value, y = Dataset), color = '#B1805B', fill = '#B1805B') +
  theme_minimal() + 
  labs(title = 'Minimal RMSE',
       subtitle = 'for different regression tasks',
       x = 'RMSE',
       y = 'Dataset',
       color = 'Removal strategy',
       fill  = 'Removal strategy') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  xlim(0, NA) +
  scale_y_discrete(position = "right") +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_blank(),
        axis.title.x  = element_text(colour = 'black', size = 12),
        axis.title.y  = element_blank(),
        axis.text.y   = element_text(colour = "black", size = 9),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "none",
        strip.text.y.right = element_text(angle = 0))


((h1 / i1) | (plot_spacer() / plot_spacer()) | (l1 / n1) | (m1 / o1)) + plot_layout(widths = c(5, 0.5, 4, 4))
```

### Binary classification

```{r echo=FALSE}
all_engines_bin_fs_only <- all_engines_bin_fs[all_engines_bin_fs$Feature_selection == 'yes', ]
all_engines_reg_fs_only <- all_engines_reg_min_med_fs[all_engines_reg_min_med_fs$Feature_selection == 'yes', ]
```

```{r fig.height=6, fig.width=20, echo=FALSE, warning=FALSE}
p1 <- ggplot(data = all_engines_bin_fs_only, aes(x = Max, y = Dataset, color = factor(Removal), fill = factor(Removal))) + 
  geom_boxplot(alpha = 0.5) +
  geom_point(data = all_engines_bin_baselines[all_engines_bin_baselines$Metric == 'accuracy', ], 
             size = 5, shape = 4, aes(x = Max, y = Dataset), color = '#B1805B', fill = '#B1805B') +
  theme_minimal() + 
  labs(title = 'Max Accuracy',
       subtitle = 'with FS for different binary classification tasks',
       x = 'Value',
       y = 'Dataset',
       color = 'Removal strategy',
       fill  = 'Removal strategy') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  xlim(0.93, NA) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x  = element_blank(),
        axis.title.y  = element_blank(),
        axis.text.y   = element_text(colour = "black", size = 9),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "none",
        strip.text.y.right = element_text(angle = 0))

r1 <- ggplot(data = all_engines_bin_fs_only, aes(x = Mean, y = Dataset, color = factor(Removal), fill = factor(Removal))) + 
  geom_boxplot(alpha = 0.5) +
  geom_point(data = all_engines_bin_baselines[all_engines_bin_baselines$Metric == 'accuracy', ], 
             size = 5, shape = 4, aes(x = Mean, y = Dataset), color = '#B1805B', fill = '#B1805B') +
  theme_minimal() + 
  labs(title = 'Mean Accuracy',
       subtitle = 'with FS for different binary classification tasks',
       x = 'Value',
       y = 'Dataset',
       color = 'Removal strategy',
       fill  = 'Removal strategy') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  xlim(0.65, NA) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_blank(),
        axis.title.x  = element_blank(),
        axis.title.y  = element_blank(),
        axis.text.y   = element_text(colour = "black", size = 9),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "none",
        strip.text.y.right = element_text(angle = 0))

u1 <- ggplot(data = all_engines_reg_fs_only[all_engines_reg_fs_only$Aggregation == 'Median', ], 
             aes(x = Value, y = Dataset, color = factor(Removal), fill = factor(Removal))) + 
  geom_boxplot(alpha = 0.5) +
  geom_point(data = all_engines_reg_baselines_min_med[which(all_engines_reg_baselines_min_med$Metric == 'rmse' & 
                                                            all_engines_reg_baselines_min_med$Aggregation == 'Median'), ], 
             size = 4, shape = 4, aes(x = Value, y = Dataset), color = '#B1805B', fill = '#B1805B') +
  theme_minimal() + 
  labs(title = 'Median RMSE (Magnified)',
       subtitle = 'with FS for different regression tasks',
       x = 'RMSE',
       y = 'Dataset',
       color = 'Removal strategy',
       fill  = 'Removal strategy') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  xlim(0, 1.5) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x  = element_blank(),
        axis.title.y  = element_blank(),
        axis.text.y   = element_blank(),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "none",
        strip.text.y.right = element_text(angle = 0))

v1 <- ggplot(data = all_engines_reg_fs_only[all_engines_reg_fs_only$Aggregation == 'Median', ], 
             aes(x = Value, y = Dataset, color = factor(Removal), fill = factor(Removal))) + 
  geom_boxplot(alpha = 0.5) +
  geom_point(data = all_engines_reg_baselines_min_med[which(all_engines_reg_baselines_min_med$Metric == 'rmse' & 
                                                            all_engines_reg_baselines_min_med$Aggregation == 'Median'), ], 
             size = 4, shape = 4, aes(x = Value, y = Dataset), color = '#B1805B', fill = '#B1805B') +
  theme_minimal() + 
  labs(title = 'Median RMSE',
       subtitle = 'with FS for different regression tasks',
       x = 'RMSE',
       y = 'Dataset',
       color = 'Removal strategy',
       fill  = 'Removal strategy') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  xlim(8.5, NA) +
  scale_y_discrete(position = "right") +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_text(colour = 'black', size = 12),
        axis.title.x  = element_blank(),
        axis.title.y  = element_blank(),
        axis.text.y   = element_text(colour = "black", size = 9),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "none",
        strip.text.y.right = element_text(angle = 0))

w1 <- ggplot(data = all_engines_reg_fs_only[all_engines_reg_fs_only$Aggregation == 'Min', ], 
             aes(x = Value, y = Dataset, color = factor(Removal), fill = factor(Removal))) + 
  geom_boxplot(alpha = 0.5) +
  geom_point(data = all_engines_reg_baselines_min_med[which(all_engines_reg_baselines_min_med$Metric == 'rmse' & 
                                                            all_engines_reg_baselines_min_med$Aggregation == 'Min'), ], 
             size = 4, shape = 4, aes(x = Value, y = Dataset), color = '#B1805B', fill = '#B1805B') +
  theme_minimal() + 
  labs(title = 'Minimal RMSE (Magnified)',
       subtitle = 'with FS for different regression tasks',
       x = 'RMSE',
       y = 'Dataset',
       color = 'Removal strategy',
       fill  = 'Removal strategy') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  xlim(0, 1.5) +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_blank(),
        axis.title.x  = element_text(colour = 'black', size = 12),
        axis.title.y  = element_blank(),
        axis.text.y   = element_blank(),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "bottom",
        strip.text.y.right = element_text(angle = 0))

x1 <- ggplot(data = all_engines_reg_fs_only[all_engines_reg_fs_only$Aggregation == 'Min', ], 
             aes(x = Value, y = Dataset, color = factor(Removal), fill = factor(Removal))) + 
  geom_boxplot(alpha = 0.5) +
  geom_point(data = all_engines_reg_baselines_min_med[which(all_engines_reg_baselines_min_med$Metric == 'rmse' & 
                                                            all_engines_reg_baselines_min_med$Aggregation == 'Min'), ], 
             size = 4, shape = 4, aes(x = Value, y = Dataset), color = '#B1805B', fill = '#B1805B') +
  theme_minimal() + 
  labs(title = 'Minimal RMSE',
       subtitle = 'with FS for different regression tasks',
       x = 'RMSE',
       y = 'Dataset',
       color = 'Removal strategy',
       fill  = 'Removal strategy') +
  scale_color_manual(values = c("#74533d", "#afc968", "#7C843C", "#B1805B")) +
  scale_fill_manual(values  = c("#74533d", "#afc968",  "#7C843C", "#B1805B")) +
  xlim(0, NA) +
  scale_y_discrete(position = "right") +
  theme(plot.title    = element_text(colour = 'black', size = 15),
        plot.subtitle = element_blank(),
        axis.title.x  = element_text(colour = 'black', size = 12),
        axis.title.y  = element_blank(),
        axis.text.y   = element_text(colour = "black", size = 9),
        axis.text.x   = element_text(colour = "black", size = 9)) + 
  theme(strip.background   = element_rect(fill = "white", color = "white"),
        strip.text         = element_text(size = 6 ), 
        legend.position    = "none",
        strip.text.y.right = element_text(angle = 0))

((p1 / r1) | (plot_spacer() / plot_spacer()) | (u1 / w1) | (v1 / x1)) + plot_layout(widths = c(5, 0.5, 4, 4))
```
