---
title: "Ablation study of forester: Model training"
author: "Hubert Ruczyński"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_collapsed: yes
    theme: lumen
    toc_depth: 3
    number_sections: yes
    latex_engine: xelatex
---

```{css, echo=FALSE}
body .main-container {
  max-width: 1820px !important;
  width: 1820px !important;
}
body {
  max-width: 1820px !important;
  width: 1820px !important;
  font-family: Helvetica !important;
  font-size: 16pt !important;
}
h1,h2,h3,h4,h5,h6{
  font-size: 24pt !important;
}
```

# Downloads

The necessary downloads required for the forester package to work properly, if downloaded, the user can skip this part.

```{r eval = FALSE}
install.packages("devtools")
devtools::install_github("ModelOriented/forester")
devtools::install_github('catboost/catboost', subdir = 'catboost/R-package')
devtools::install_github('ricardo-bion/ggradar', dependencies = TRUE)
install.packages('tinytex')
tinytex::install_tinytex()
```

# Imports

Importing the necessary libraries.

```{r warning=FALSE, message=FALSE}
library(forester)
```

# Import of outcomes

At this step we import the outcomes obtained by the `ablation_study_preprocessing` .

```{r}
files <- list.files('ablation_preprocessing_data', pattern = 'RData')
data  <- list()
for (i in 1:length(files)) {
  data[[i]] <- readRDS(paste0('ablation_preprocessing_data/', files[i]))
}
```

# Training

## Parameters preparation

We copy the parameters vectors from the `ablation_study_preprocessing` to use them for naming new outcomes.

```{r}
imp_method <- c('median-other', 'median-other',     'median-other',                 # RM
                'median-other', 'median-frequency', 'knn',          'mice',         # Imp
                'median-other', 'median-other',     'median-other', 'median-other', # FS
                'median-other', 'median-frequency', 'knn',          'mice',         # RM + Imp 
                'median-other', 'median-frequency', 'knn',          'mice',         # RM + Imp 
                'median-other', 'median-other',     'median-other', 'median-other', # RM + FS
                'median-other', 'median-other',     'median-other', 'median-other', # RM + FS
                'median-other', 'knn',              'median-other', 'knn',          # Imp + FS 
                'median-other', 'knn',              'median-other', 'knn',          # RM + Imp + FS 
                'median-other', 'knn',              'median-other', 'knn')          # RM + Imp + FS

fs_method <- c('none', 'none', 'none',             # RM
               'none', 'none', 'none',   'none',   # Imp
               'VI',   'MCFS', 'MI',     'BORUTA', # FS
               'none', 'none', 'none',   'none',   # RM + Imp 
               'none', 'none', 'none',   'none',   # RM + Imp 
               'VI',   'MCFS', 'MI',     'BORUTA', # RM + FS
               'VI',   'MCFS', 'MI',     'BORUTA', # RM + FS
               'VI',   'VI',   'BORUTA', 'BORUTA', # Imp + FS 
               'VI',   'VI',   'BORUTA', 'BORUTA', # RM + Imp + FS
               'VI',   'VI',   'BORUTA', 'BORUTA') # RM + Imp + FS

rmv_names <- c('removal_min', 'removal_med', 'removal_max',                # RM
               'removal_min', 'removal_min', 'removal_min', 'removal_min', # Imp
               'removal_min', 'removal_min', 'removal_min', 'removal_min', # FS
               'removal_med', 'removal_med', 'removal_med', 'removal_med', # RM + Imp 
               'removal_max', 'removal_max', 'removal_max', 'removal_max', # RM + Imp
               'removal_med', 'removal_med', 'removal_med', 'removal_med', # RM + FS
               'removal_max', 'removal_max', 'removal_max', 'removal_max', # RM + FS
               'removal_min', 'removal_min', 'removal_min', 'removal_min', # Imp + FS 
               'removal_med', 'removal_med', 'removal_med', 'removal_med', # RM + Imp + FS 
               'removal_max', 'removal_max', 'removal_max', 'removal_max') # RM + Imp + FS
```

## Training function for a single dataset

This function performs a training for a single major dataset like `banknote-authentication` , so it results in training 39 models 1 per each preprocessed dataset. Function parameters are similar to the function conducting the preprocessing in `ablation_study_preprocessing` script, and it follows the same saving pattern.

```{r}
single_dataset_training <- function(data, y, imp_method, fs_method, rmv_names, dataset_name, binary = TRUE, verbose = 'part') {
  list_times  <- c()
  names_times <- c()
  out_data    <- list()
  
  if (verbose == 'part') {
    text_verbose <- TRUE
    exp_verbose  <- FALSE
  } else if (verbose == 'all') {
    text_verbose <- TRUE
    exp_verbose  <- TRUE
  } else if (verbose == 'none') {
    text_verbose <- FALSE
    exp_verbose  <- FALSE
  }
  
  # Create directory for the training results of the ablation study, if it exists
  # nothing happens.
  dir.create('ablation_results', showWarnings = FALSE)
  
  # Create subdirectories for separate tasks, and attempt to read the lists of
  # durations spent on the trainig. If error araises it means we have no proper
  # files, thus we create them from scratch.
  if (binary) {
    dir.create(paste0('ablation_results/binary_', dataset_name), showWarnings = FALSE)
    tryCatch({
      suppressWarnings(list_times  <- readRDS(paste0(getwd(), '/ablation_results/binary_', dataset_name, '/list_times.RData')))
      suppressWarnings(names_times <- readRDS(paste0(getwd(), '/ablation_results/binary_', dataset_name, '/names_times.RData')))
      print('Loaded times list.')
    }, error = function(cond) {
      print('No times list.')
    })
  } else {
    dir.create(paste0('ablation_results/regression_', dataset_name), showWarnings = FALSE)
    tryCatch({
      suppressWarnings(list_times  <- readRDS(paste0(getwd(), '/ablation_results/regression_', dataset_name, '/list_times.RData')))
      suppressWarnings(names_times <- readRDS(paste0(getwd(), '/ablation_results/regression_', dataset_name, '/names_times.RData')))
      print('Loaded times list.')
    }, error = function(cond) {
      print('No times list.')
    })
  }
  # Iterate through differently prepared datsets and train the forester on them.
  for (i in 1:39) {
    verbose_cat('\n Iteration:', i, 'Removal:', rmv_names[i], 'Imputation:', 
                imp_method[i], 'Feature Selection:', fs_method[i], '\n', verbose = text_verbose)
    
    # We train new models only if we don't have an outcome for provided dataset.
    if (!file.exists(paste0('ablation_results/binary_', dataset_name, '/', i, '.RData')) &&
        !file.exists(paste0('ablation_results/regression_', dataset_name, '/', i,  '.RData'))) {
        # Calculate start end stop times for each training.
        start          <- as.numeric(Sys.time())
        names_times[i] <- paste0('Training: ', dataset_name, ' Removal: ', rmv_names[i], 
                                 ' Imputation: ', imp_method[i], ' Feature Selection: ', fs_method[i])
        script_wd      <- getwd()
        
        outcomes <- train(data                 = data$prep_data[[i]]$data, 
                          y                    = y,
                          engine               = c('ranger', 'xgboost', 'decision_tree', 'lightgbm', 'catboost'),
                          verbose              = exp_verbose,
                          train_test_split     = c(0.6, 0.2, 0.2),
                          split_seed           = 123,
                          bayes_iter           = 0,
                          random_evals         = 20,
                          custom_preprocessing = data$prep_data[[i]])

        setwd(script_wd)
        stop          <- as.numeric(Sys.time())
        # Insert only the time spent on a singular training. As we can see it won't
        # be appended but will replace the previous value, so if for some reason we
        # delete the result we will get new time here.
        list_times[i] <- round(stop - start, 1)
        #out_data[[i]] <- outcomes
        out_data[[i]] <- NULL
        
        # Save new outcomes as a new file and re-save both list_times and names_times.
        if (binary) {
          saveRDS(outcomes,    paste0(getwd(), '/ablation_results/binary_', dataset_name, '/', i, '.RData'))
          saveRDS(list_times,  paste0(getwd(), '/ablation_results/binary_', dataset_name, '/list_times.RData'))
          saveRDS(names_times, paste0(getwd(), '/ablation_results/binary_', dataset_name, '/names_times.RData'))
        } else {
          saveRDS(outcomes,    paste0(getwd(), '/ablation_results/regression_', dataset_name, '/', i, '.RData'))
          saveRDS(list_times,  paste0(getwd(), '/ablation_results/regression_', dataset_name, '/list_times.RData'))
          saveRDS(names_times, paste0(getwd(), '/ablation_results/regression_', dataset_name, '/names_times.RData'))
        }
    # When we already have the outcomes, we don't have to load the times, as they are already ok.
    } else if (binary) {
      #out_data[[i]] <- readRDS(paste0(getwd(), '/ablation_results/binary_', dataset_name, '/', i, '.RData'))
      out_data[[i]] <- NULL
    } else{
      #out_data[[i]] <- readRDS(paste0(getwd(), '/ablation_results/regression_', dataset_name, '/', i, '.RData'))
      out_data[[i]] <- NULL
    }
  }
  #names(out_data) <- names_times
  time_df         <- data.frame(name = names_times, duration = list_times)
  
  outcome <- list(
    time_df  = time_df,
    out_data = out_data
  )
  
  if (binary) {
    saveRDS(outcome, paste0('ablation_results/binary_', dataset_name, '.RData'))
  } else {
    saveRDS(outcome, paste0('ablation_results/regression_', dataset_name, '.RData'))
  }
}

```

# All datasets training

In this section we present the function conducting multiple training for different datasets.

## Parameters preparation

Firstly we prepare lists of additional parameters describing the datasets.

```{r}
targets_binary     <- c('Class', 'Class', 'Class', 'class', 'class', 'class', 'class', 'Class')
targets_regression <- c('y', 'rej', 'Goal', 'y', 'y', 'foo', 'quality')
names_binary       <- c('banknote-authentication', 'blood-transfusion-service-center',
                        'breast-w', 'credit-approval', 'credit-g', 'diabetes',  
                        'kr-vs-kp', 'phoneme')
names_regression   <- c('2dplanes', 'bank32nh', 'elevators', 'kin8nm', 
                        'Mercedes_Benz_Greener_Manufacturing', 'pol', 'wine_quality')
```

## Multiple training

The function is similar to the previous one, and it helps with executing the preprocessing of multiple datasets at once.

```{r}
multiple_training <- function(data, targets, imp_method, fs_method, rmv_names, dataset_names, binary = TRUE, verbose = 'part') {
  
  if (verbose == 'part') {
    text_verbose <- TRUE
  } else if (verbose == 'all') {
    text_verbose <- TRUE
  } else if (verbose == 'none') {
    text_verbose <- FALSE
  }
  
  for (i in 1:length(data)) {
    if (!file.exists(paste0('ablation_results/binary_', dataset_names[i], '.RData')) &&
        !file.exists(paste0('ablation_results/regression_', dataset_names[i], '.RData'))) {
      
      verbose_cat('The results file for the', i, 'dataset, called', dataset_names[i], 
                  'does not exist, proceeding with preprocessing.\n', verbose = text_verbose)
      
      single_dataset_training(data         = data[[i]], 
                              y            = targets[i], 
                              imp_method   = imp_method, 
                              fs_method    = fs_method, 
                              rmv_names    = rmv_names, 
                              dataset_name = dataset_names[i], 
                              binary       = binary,
                              verbose      = verbose)
    } else {
      verbose_cat('The results file for the', i, 'dataset, called', dataset_names[i], 
                  'exists, skipping the preprocessing.\n', verbose = text_verbose)
    }
  }
}
```

# Training execution

The code executing the training for both binary classification and regression tasks.

## Binary

```{r eval = FALSE}
multiple_training(data          = data[1:8], 
                  targets       = targets_binary, 
                  imp_method    = imp_method, 
                  fs_method     = fs_method, 
                  rmv_names     = rmv_names, 
                  dataset_names = names_binary, 
                  binary        = TRUE, 
                  verbose       = 'part')
```

## Regression

```{r eval = FALSE}
multiple_training(data          = data[9:15],
                  targets       = targets_regression,
                  imp_method    = imp_method, 
                  fs_method     = fs_method, 
                  rmv_names     = rmv_names, 
                  dataset_names = names_regression,
                  binary        = FALSE, 
                  verbose       = 'part')
```

## Tests

```{r}
k <- readRDS('ablation_results/binary_banknote-authentication.RData')
```

```{r}
rmarkdown::paged_table(k$time_df)
```

```{r}
rmarkdown::paged_table(k$out_data$`Training: banknote-authentication Removal: removal_min Imputation: median-other Feature Selection: none`$score_valid)
```

```{r}
rmarkdown::paged_table(k$out_data$`Training: banknote-authentication Removal: removal_max Imputation: knn Feature Selection: BORUTA`$score_valid)
```
